---
output: html_document
editor_options: 
  chunk_output_type: inline
---
```{r setup, include=FALSE} 
knitr::opts_chunk$set(warning = FALSE, message = FALSE) 
```

```{r,  results="hide"}
library(tidyverse)
library(ggplot2)
library(plyr)
library(dplyr)
library(readr)
library(readxl)
library(ggpubr)
library(stringi)
library(tidyr)
library(reshape2)
library(vegan)
library(parallel)
library(Biostrings)
library(gRodon)
```

wget https://data.gtdb.ecogenomic.org/releases/release202/202.0/genomic_files_reps/bac120_ssu_reps_r202.tar.gz
tar -xzf bac120_ssu_reps_r202.tar.gz
usearch -makeudb_usearch *.fna -output db.udb

usearch -usearch_global ASVs.fasta -db db.udb -id 0.97  -evalue 1e-6 \
-strand both  -maxaccepts 0 -maxrejects 0   \
-threads 35  -blast6out  ASV_GTDB.mapped_global.txt

Unfortunately the size of the genome files is to be big to be uploaded in a github 
repo

Please change the working directory "setwd( "yourpath")" to your 
directory if you want to run the code from the next parts.


```{r,  results="hide"}
matches= read.delim(file =  "../16S_ASVdada2/ASV_GTDB.mapped_global.txt", header = F)
matches$codname=gsub(" d_*.*","", matches$V2)

matches$genome=paste0( gsub("RS_","", gsub("GB_","", matches$codname)))
write.table(unique( matches$genome), file =  "../OutputData/codenames.txt", 
            row.names = F, quote=F)
all_models_dif=read.csv("../OutputData/TableS3_RespondersPlot.csv_revised")
```

**Download the genomes**
filename='codenames.txt'
while read i;
   do 
   echo "$i"

  datasets download genome accession "$i" --filename "$i"_dataset.zip
     
done <"$filename"
 
***Run in a SLURM***
***Find the NCBI datasets and save the files in a location***

#!/bin/bash
#SBATCH --job-name=ncbi_downloads
#SBATCH --chdir=/YOURPATHHERE
#SBATCH --output=/work/%u/%x-%A-%a.log
#SBATCH --cpus-per-task=5
#SBATCH --time=20:20:00
#SBATCH --mem-per-cpu=5G

module purge
module load Conda/24.3.0
conda activate ncbi_datasets

#Author: Ioannis Kampouris
#Purpose: download mapped genomes from GTDB from NCBI
#Dependencies: datasets  from NCBI

filename="codenames.txt"
mkdir genomes

while read i;
   do
   echo "$i"

  datasets download genome accession "$i" --filename genomes/"$i"_dataset.zip

done <"$filename 

**Run PROKKA**
#!/bin/bash
#SBATCH --job-name=prokka_genomerunner_array
#SBATCH --chdir="YOURPATHHERE"
#SBATCH --output=/work/%u/%x-%A-%a.log
#SBATCH --cpus-per-task=3
#SBATCH --time=5:00:00
#SBATCH --array=1-10528
#SBATCH --mem-per-cpu=10G


#Author: Ioannis Kampouris
#Purpose: Perform Prokka
module load GCC/12.2.0 OpenMPI/4.1.4 prokka/1.14.5


input_files="/work/kampouri/MS7/genomepaths.txt"
input_file=$(awk "NR==$SLURM_ARRAY_TASK_ID" "$input_files")
prokka ${input_file} -o ${input_file}_prokka  \
 --cpus "${SLURM_CPUS_PER_TASK:-1}" --dbdir /data/db/prokka --force


Us this script to gather all annotated files:

#!/bin/bash
#SBATCH --job-name=MS7_gather_genomes
#SBATCH --chdir="YOURPATHHERE"
#SBATCH --output=/work/%u/%x-%A-%a.log
#SBATCH --cpus-per-task=2
#SBATCH --time=01:30:00
#SBATCH --mem-per-cpu=10G

rm -rf all_prokka_files
mkdir all_prokka_files

cd "YOURPATHHERE"
for i in  genomes/unzipped/*/*/*/*/*/*.ffn
do

new=$(echo ${i} | sed 's/.*.ncbi_dataset.data.//g')
new=$(echo ${new} | sed 's/\//_/g')
echo "$new"
cp -f "$i" all_prokka_files/"$new"

done

```{r, warning=FALSE}
path="../../MS7_all_prokka_files"
list1=list.files(path, pattern="*ffn", recursive = TRUE)

all_pds=function(x) {

path_to_genome <- paste0(path, "/",list1[x])
genes <- Biostrings::readDNAStringSet(path_to_genome)

#Search for genes annotated as ribosomal proteins
highly_expressed <- grepl("ribosomal protein",names(genes),ignore.case = T)
pd1= gRodon::predictGrowth(genes, highly_expressed, mode="partial")
pd2=pd1$d
pd3=data.frame(G1=paste0(list1[x]), DoublingTime=pd2)
return(pd3)
}
results <- mclapply( 1:length(list1), function(x) all_pds(x), mc.cores = 24)
results2=do.call("rbind",results)%>%separate(., col=G1, into=c("Genome","PR"),
                                             sep="_prokka")%>%
  mutate(genome=str_replace(Genome,"_G.*", ""))
matches2=full_join(matches, results2) 
matches3=filter(matches2, DoublingTime!="NA")



write.csv(file = "../OutputData/All_Growth_Rates_for_All_mapped_ASVs.csv",
          matches3)

```


#!/bin/bash
#SBATCH --job-name=running_diamond_for_dbCAN
#SBATCH --chdir="YOURPATHHERE"
#SBATCH --output=/work/%u/%x-%A-%a.log
#SBATCH --cpus-per-task=8
#SBATCH --time=01:35:00
#SBATCH --array=1-10528
#SBATCH --mem-per-cpu=5G


module purge
module load GCC/12.2.0
module load DIAMOND/2.1.8
#Author: Ioannis Kampouris
#Purpose: perform diamond to annotate the genes as Cazyme associated genes
#Dependencies: DBCAN3 database and diamond



input_files="/work/kampouri/MS7/prodigal.listed.genes.txt"
input_file=$(awk "NR==$SLURM_ARRAY_TASK_ID" "$input_files")
diamond  blastp --query ${input_file}  -o ${input_file}_CAZYmes.txt -d \
 /YOURPATHHERE/cazydb/dbcan3_db.dmnd --id 80 \
 --query-cover 30  -k 1 -e 0.000000001 \
   --tmpdir YOURPATHHERE--threads 8

#!/bin/bash
#SBATCH --job-name=MS7_gather_genomes
#SBATCH --chdir=YOURPATHHERE
#SBATCH --output=/work/%u/%x-%A-%a.log
#SBATCH --cpus-per-task=2
#SBATCH --time=01:30:00
#SBATCH --mem-per-cpu=10G

rm -rf all_dbcan_files
mkdir all_dbcan_files

cd YOURPATHHERE
for i in  genomes/unzipped/*/*/*/*/*/*CAZYmes.txt
do

new=$(echo ${i} | sed 's/.*.ncbi_dataset.data.//g')
new=$(echo ${new} | sed 's/\//_/g')
echo "$new"
cp -f "$i" all_dbcan_files/"$new"

done

```{r}
path="../../MS7_all_dbcan_files"
list1=list.files(path, pattern="*txt", recursive = TRUE)
all_dbcans=function(x) {
path_to_genome <- paste0(path, "/",list1[x])
if (file.info(path_to_genome)$size>0){
file1=read.delim(path_to_genome, header = F)
file2=data.frame(G1=paste0(list1[x]), CazymeGenes=nrow(file1))}else{
  file2=data.frame(G1=paste0(list1[x]), CazymeGenes=0)
}
return(file2)
}
resultscazy <- mclapply( 1:length(list1), 
                         function(x) all_dbcans(x), mc.cores = 24)
results2cazy=do.call("rbind",resultscazy)%>%
  separate(., col=G1, into=c("Genome","PR"),
sep="_prokka")%>%
  mutate(genome=str_replace(Genome,"_G.*", ""))%>%
    select(genome, CazymeGenes)

```
Run this code to gather the genomes first in a SLURM system

#!/bin/bash
#SBATCH --job-name=MS7_gather_genomes
#SBATCH --chdir=YOURPATHHERE
#SBATCH --output=/work/%u/%x-%A-%a.log
#SBATCH --cpus-per-task=2
#SBATCH --time=01:30:00
#SBATCH --mem-per-cpu=10G

rm -rf all_genomes
mkdir all_genomes

cd YOURPATHHERE
for i in  genomes/unzipped/G*/nc*/da*/G*/G*.fna
do

new=$(echo ${i} | sed 's/.*.ncbi_dataset.data.//g')
new=$(echo ${new} | sed 's/\//_/g')
echo "$new"
cp -f "$i" all_genomes/"$new"

done



Run the code for the analysis in a slurm system using checkM2:
Running time: ~48 hours

#!/bin/bash
#SBATCH --job-name=GTDB_tk_runner
#SBATCH --chdir=YOURPATHHERE
#SBATCH --output=/work/%u/%x-%A-%a.log
#SBATCH --cpus-per-task=30
#SBATCH --time=42:20:00
#SBATCH --mem-per-cpu=10G



#Author: Ioannis Kampouris
#Purpose: Perform CheckM2 on selected genomes

module purge
module load Conda/25.3.1
conda activate /data/luclivir/checkm2

checkm2 predict --input all_genomes  --output-directory checkM2_output
--database_path /YOURPATHHERE/CheckM2_database/uniref100.KO.1.dmnd 
--threads 30  --tmpdir "YOURPATHHERE"--force

```{r}
genome_size=read.delim("../InputData/genomesizecheckM2.tsv")%>%
  select(Genome=Name, Genome_Size,Completeness, Contamination)%>%
  mutate(genome=str_replace(Genome,"_G.*", ""))%>%
    select(genome, Genome_Size,Completeness, Contamination)
genome_size$Genome_Size2=genome_size$Genome_Size+
  (1-genome_size$Completeness/100)*genome_size$Genome_Size-
  (genome_size$Contamination/100)*genome_size$Genome_Size

matches3B=full_join(results2cazy, matches3)
matches3C=full_join(genome_size, matches3B)

write.csv( 
    "../OutputData/All_ASVs_Tillage_GMs_Growth_rates_GenomeSize_CazymeGenes.csv",
          matches3C)

matches5=full_join( all_models_dif, 
select(matches3C, ASV=V1, everything()))
matches5$till2=matches5$coeff
matches5$till2[matches5$till2>0]="MP"
matches5$till2[matches5$till2!="MP"]="CT"
matches5=na.omit(matches5)
matches5$till3=ifelse(matches5$till2 == "CT", 0, 1)
```

Save the growth rates data in a single file.
Note:
Originally this script was one, but the genomes size is to big to be uploaded 
in GitHub.

```{r}
write.csv(file = 
    "../OutputData/Tillage_GMs_Growth_rates_GenomeSize_CazymeGenes.csv",
          matches5)

```


```{r}
print(paste0("The end!!!"))
```


 