---
output: html_document
editor_options: 
  chunk_output_type: inline
---
```{r setup, include=FALSE} 
knitr::opts_chunk$set(warning = FALSE, message = FALSE) 
```

```{r,  results="hide"}
library(tidyverse)
library(ggplot2)
library(plyr)
library(dplyr)
library(readr)
library(readxl)
library(ggpubr)
library(stringi)
library(tidyr)
library(reshape2)
library(vegan)
library(parallel)
library(Biostrings)
library(gRodon)
library(introdataviz)
```

wget https://data.gtdb.ecogenomic.org/releases/release202/202.0/genomic_files_reps/bac120_ssu_reps_r202.tar.gz
tar -xzf bac120_ssu_reps_r202.tar.gz
usearch -makeudb_usearch *.fna -output db.udb

usearch -usearch_global diff_ab_ASVs.fa -db db.udb -id 0.97  -evalue 1e-6 \
-strand both  -maxaccepts 0 -maxrejects 0   \
-threads 35  -blast6out  ASV_GTDB.mapped_global.txt



Unfortunately the size of the genome files is to be big to be uploaded in a github 
repo
Please change "setwd( "/home/ioannis.kampouris/MLE_16S")" to your 
directory if you want to run the code from the next parts.


```{r,  results="hide"}


matches= read.delim(file =  "../16S_ASVdada2/ASV_GTDB.mapped_global.txt", header = F)
matches$codname=gsub(" d_*.*","", matches$V2)

matches$genome=paste0( gsub("RS_","", gsub("GB_","", matches$codname)))
write.table(unique( matches$genome), file =  "../OutputData/codenames.txt", 
            row.names = F, quote=F)
all_models_dif=read.csv("../OutputData/TableS3_RespondersPlot.csv_revised")

```

**Download the genomes**
filename='codenames.txt'
while read i;
   do 
   echo "$i"

  datasets download genome accession "$i" --filename "$i"_dataset.zip
     
done <"$filename"
 
***Run in Bash***
***Find the NCBI datasets and save the files in a location***

find . -name "*.zip" -exec unzip -o {} -d  \;
genome size command :
 checkm2 predict  --input repo1 -o size1 --threads 20 -x fasta
 

**Run PROKKA**
for i in *zip; do S=$(echo ${i} | sed "s/.zip//g"); unzip "$i" -o  -d  unzipped/"$S"  ; done

mkdir prok1
ls | grep "dataset" > list_g.txt
filename='list_g.txt'
while read i; 
 do 
  do S=$(echo ${i} | sed "s/_dataset//g")
  echo "$i"
  echo "$S"
    prokka "$i"/ncbi_dataset/data/"$S"/*fna -o prok1/"$i" -prefix "$i" --cpus 30
done

```{r, warning=FALSE}
path="/../../all_prokka_files"
list1=list.files(path, pattern="*ffn", recursive = TRUE)

all_pds=function(x) {

path_to_genome <- paste0(path, "/",list1[x])
genes <- Biostrings::readDNAStringSet(path_to_genome)

#Search for genes annotated as ribosomal proteins
highly_expressed <- grepl("ribosomal protein",names(genes),ignore.case = T)
pd1= gRodon::predictGrowth(genes, highly_expressed, mode="partial")
pd2=pd1$d
pd3=data.frame(G1=paste0(list1[x]), DoublingTime=pd2)
return(pd3)
}
results <- mclapply( 1:length(list1), function(x) all_pds(x), mc.cores = 24)
results2=do.call("rbind",results)%>%separate(., col=G1, into=c("Genome","PR"),
                                             sep="_prokka")%>%
  mutate(genome=str_replace(Genome,"_G.*", ""))
matches2=full_join(matches, results2) 
matches3=filter(matches2, DoublingTime!="NA")



write.csv(file = "../OutputData/All_Growth_Rates_for_All_mapped_ASVs.csv",
          matches3)

```

```{r}
path="/../../_all_dbcan_files"
list1=list.files(path, pattern="*txt", recursive = TRUE)

all_dbcans=function(x) {

path_to_genome <- paste0(path, "/",list1[x])
if (file.info(path_to_genome)$size>0){

file1=read.delim(path_to_genome, header = F)

file2=data.frame(G1=paste0(list1[x]), CazymeGenes=nrow(file1))}else{
  file2=data.frame(G1=paste0(list1[x]), CazymeGenes=0)
}
return(file2)
}

resultscazy <- mclapply( 1:length(list1), function(x) all_dbcans(x), mc.cores = 24)
results2cazy=do.call("rbind",resultscazy)%>%separate(., col=G1, into=c("Genome","PR"),
                                             sep="_prokka")%>%
  mutate(genome=str_replace(Genome,"_G.*", ""))%>%
    select(genome, CazymeGenes)

genome_size=read.delim("/vol/IDK3/MS7_new/genomesizecheckM2.tsv")%>%
  select(Genome=Name, Genome_Size,Completeness, Contamination)%>%
  mutate(genome=str_replace(Genome,"_G.*", ""))%>%
    select(genome, Genome_Size,Completeness, Contamination)
genome_size$Genome_Size2=genome_size$Genome_Size+(1-genome_size$Completeness/100)*genome_size$Genome_Size-(genome_size$Contamination/100)*genome_size$Genome_Size

matches3B=full_join(results2cazy, matches3)
matches3C=full_join(genome_size, matches3B)

matches5=full_join( all_models_dif, 
select(matches3C, ASV=V1, everything()))
matches5$till2=matches5$coeff
matches5$till2[matches5$till2>0]="MP"
matches5$till2[matches5$till2!="MP"]="CT"
matches5=na.omit(matches5)
matches5$till3=ifelse(matches5$till2 == "CT", 0, 1)

```

Save the growth rates data in a single file.
Note:
Originally this script was one, but the genomes size is to big to be uploaded 
in GitHub.

```{r}
write.csv(file = "../OutputData/Tillage_GMs_Growth_rates_GenomeSize_CazymeGenes.csv",
          matches5)

```
```{r}
print(paste0("The end!!!"))
```
matches6=dcast(matches5, ASV+Soil_Type+Year+FC~., value.var = "DoublingTime", median)
ggplot(matches6, aes(x=FC, y=(`.`), colour=Soil_Type))+geom_smooth(method = "lm")+stat_cor(method = "spearman")+facet_wrap(~Year)+geom_point()


 