```{r}
library(tidyverse)
library(ggplot2)
library(plyr)
library(dplyr)
library(readr)
library(readxl)
library(ggpubr)
library(stringi)
library(tidyr)
library(reshape2)
library(vegan)
library(parallel)
library(lme4)
library(ggtext)
library(boot)
```

Upload the nutrient table
```{r}
nutrients1=read.csv(file.path("../InputData", "soil_lab.csv"), check.names=F)
```

Change the names of the variable accordingly 
```{r}
nutrients1$TILLAGE2=nutrients1$Tillage
nutrients1$FERTILIZATION2=nutrients1$Fertilization
nutrients1$TILLAGE2=ifelse(nutrients1$TILLAGE2 == "Cultivator", 0, 1)
nutrients1$FERTILIZATION2=ifelse(nutrients1$FERTILIZATION2 == "extensive", 0, 1)
```

prepare the nutrients data for our model 
```{r}
rownames(nutrients1)=paste0(nutrients1$TILLAGE2,"_",
                             nutrients1$FERTILIZATION2,"_",
                             nutrients1$Block,"_",
                             nutrients1$Experimental_Year)
nutrients1=as.data.frame(nutrients1)
nutrients2=nutrients1[rownames(nutrients1),6:21, drop=F]
nutrients2=as.data.frame(apply(nutrients2, 2, function(x) replace(x, is.na(x), mean(x, na.rm = TRUE))))
nutrients2=(nutrients2)
nutrients1[rownames(nutrients1),6:21]=nutrients2
nutrients3=gather(nutrients1,
  -c(colnames(nutrients1[rownames(nutrients1),
  c(1:5, 22:ncol(nutrients1))])),
  key ="Nutrient",
  value = "Variable")

nutrients4= nutrients3 %>% filter(Nutrient %in% c("N[%]", "OM[%]"))
nutrients4$G=paste0(nutrients4$Tillage,";", nutrients4$Fertilization)
```
Dunn's test for Nitrogen and Carbon 
```{r}
Letter_list=list()
for( i in unique(nutrients4$Nutrient)){
for( j in unique(nutrients4$Experimental_Year)){

file1=filter(nutrients4, Nutrient==i&Experimental_Year==j)
dunns= dunn.test::dunn.test(file1$Variable, file1$G, method = "BH")
comparisons=data.frame(comparisons=dunns$comparisons, p=dunns$P.adjusted)%>%
  separate(., "comparisons", into = c("row","col"), sep = " - ")
orderlist= aggregate( file1, Variable~G, mean)
comparisons=full_join(comparisons, orderlist%>%mutate(row=G), by="row")%>%
  na.omit()
comparisons=comparisons[order(comparisons$Variable, decreasing = T),]
names1=paste0(comparisons$row,"-", comparisons$col)
p=comparisons$p
names(p)=names1
letters=  multcompView::multcompLetters(p,  
compare = "<", reversed =F)$Letters%>%as.data.frame()
colnames(letters)="L1"
letters$G=rownames(letters)
letters$Experimental_Year=j
letters$Nutrient=paste0(i)
Letter_list=rbind(letters, Letter_list)  
}}

```


Plot the Soil and Nitrogen concentrations.
```{r}

nutrients4$Tillage=gsub("Cultivator","CT",
  gsub("Plough", "MP", nutrients4$Tillage)
)
nutrients4$Fertilization=gsub("extensive","Ext.",
  gsub("intensive", "Int.", nutrients4$Fertilization)
)

nutrients4$Nutrient_label=factor(
  nutrients4$Nutrient,
  levels = c("OM[%]","N[%]"),
  labels = c(expression(paste("SOM (%)")),
              expression(paste("N (%)"))
            )
)

nutrients5<-dcast(nutrients4, Experimental_Year+Tillage+G+Fertilization+Nutrient~., 
                  value.var =  "Variable", mean)%>%select(Variable=".",
                                             everything())%>%full_join(Letter_list)

nutrients5$Nutrient_label=factor(
  nutrients5$Nutrient,
  levels = c("OM[%]","N[%]"),
  labels = c(expression(paste("SOM (%)")),
              expression(paste("N (%)"))
            ))

plot1 = ggplot(data=nutrients5, 
           aes(x = as.factor(Experimental_Year), y=Variable, fill=paste0(Tillage,"-",Fertilization))) +
  geom_bar( colour="black",
           stat="summary", position=position_dodge(width=0.9), alpha=0.6) +
  geom_point(data=nutrients4, 
             aes(x=as.factor(Experimental_Year), y=Variable, fill=paste0(Tillage,"-",Fertilization)), 
             position=position_jitterdodge (jitter.width=0.25,
                                            dodge.width =0.9 ), shape=21,
             alpha=0.7, size=2) +
  facet_wrap(~Nutrient_label, strip.position="left", scales="free", labeller=label_parsed) +
  scale_alpha_manual(values = c(1, 0.1), name="N. Fert.: ") +
  scale_fill_manual(values = c("#c8e9df","#4ab795", "#fdb79c",  "#fb6328"), name="") +
  theme_bw() +
  ylab("") +
  xlab("") +
  theme(strip.background=element_rect(fill="white", colour="white"), strip.placement = "outside") +
  theme(strip.text=element_text(size=25,colour="black")) +
  
  theme(axis.text.x=element_text(size=25,colour="black")) +
  theme(axis.text.y=element_text(size=25,colour="black")) +
  theme(axis.title.x=element_text(size=25,colour="black")) +
  
  theme(legend.text=element_text(size=25,colour="black")) + 
  theme(legend.title=element_text(size=25,colour="black")) + 
  theme(legend.position="top",axis.title.y=element_text(size=25,colour="black")) + 
  theme(legend.key.size=unit(2,"cm")) +

  guides(alpha = guide_legend(override.aes = list(fill="black")))+
    geom_text(stat = "summary", 
aes(y=Variable*1.05, label=L1), size=9, position = position_dodge(width = 1))
```

Create the mixed effect model function with year as random effect 
```{r}
mixed_effects=list()
model_coeffs=list()
for(i in unique(paste0(nutrients4$Nutrient))){
  file1=dplyr::filter(nutrients4, Nutrient==paste0(i)) 
  file1$G=paste0(file1$Fertilization,";",file1$Tillage)
  file1$Experimental_Year=as.factor(file1$Experimental_Year)
  file1$Variable=scale(file1$Variable)
  file2=lme4::lmer(Variable~TILLAGE2*FERTILIZATION2+(1|Experimental_Year), data=file1)
  
  var_corr <- VarCorr(file2)
  std_dev_experimental_year <- attr(var_corr$Experimental_Year, "stddev")
  var_experimental_year <- std_dev_experimental_year^2
  
  #Apply Bootstrap for inferring p-values and 95% CI
  boot.out = bootMer(file2, fixef, seed=11122022, nsim=10000, parallel = "multicore", ncpus = 20) 
  print("Boot  finished")

  CI.lower = apply(boot.out$t, 2, function(x) as.numeric(quantile(x, probs=.025, na.rm=TRUE)))
  CI.upper = apply(boot.out$t, 2, function(x) as.numeric(quantile(x, probs=.975, na.rm=TRUE)))
  
                                                        
  file3=as.data.frame(summary(boot.out))
  p = rbind(
    (1-apply(boot.out$t<0, 2, mean))*2,
    (1-apply(boot.out$t>0, 2, mean))*2)
  pvalues=data.frame(pval= apply(p, 2, min))
  
  # Add p_value for the model with Experimental_Year as fixed effect
  file2_fixed=lm(Variable~TILLAGE2*FERTILIZATION2*as.factor(Experimental_Year), data=file1)
  file3_fixed=summary(file2_fixed)
  file4_fixed=as.data.frame(file3_fixed$coefficients)
  file5_fixed=file4_fixed[!grepl("^as", rownames(file4_fixed)), ]
  file5_fixed <- file5_fixed %>% dplyr::rename(pval_fixed=`Pr(>|t|)`)
  file5_fixed$pval_fixed <- round(file5_fixed$pval_fixed, 4)
  
  
  file4=cbind(file3, pvalues, lower=CI.lower, upper=CI.upper, pval_fixed=file5_fixed$pval_fixed)
  
  file5=rownames_to_column(file4, var="Variable")%>%
  mutate(., Nutrient=paste0(i))
  
  
  mixed_effects=rbind(mixed_effects,file5)
  
  model_coeffs=rbind(model_coeffs, cbind(
        Nutrient=unique(file5$Nutrient),
        Singularity=isSingular(file2), 
        Var=var_experimental_year
        ))
}

mixed_effects2=filter(mixed_effects, Variable!="(Intercept)")

mixed_effects2$pval_fixed[mixed_effects2$pval_fixed<0.05]="*p* < 0.05"
mixed_effects2$pval_fixed[mixed_effects2$pval_fixed!="*p* < 0.05"]="*p* > 0.05"

mixed_effects2$pval[mixed_effects2$pval<0.05]="*p* < 0.05"
mixed_effects2$pval[mixed_effects2$pval!="*p* < 0.05"]="*p* > 0.05"
```

Create the plot for Year as random effect 
```{r}
mixed_effects2$Variable=gsub("TILLAGE2:FERTILIZATION2",
  "Interaction",mixed_effects2$Variable)

mixed_effects2$Variable=gsub("FERTILIZATION2",
  "Ext. vs Int. N-Fert.",
  gsub("TILLAGE2", "CT vs MP Tillage", mixed_effects2$Variable)
)

mixed_effects2$Variable=factor(mixed_effects2$Variable,
levels = c ("Interaction",   "Ext. vs Int. N-Fert." , "CT vs MP Tillage"              
))


model_coeffs_df <- as.data.frame(model_coeffs, stringsAsFactors = FALSE)
rownames(model_coeffs_df) <- NULL
model_coeffs_df$Var <- as.numeric(model_coeffs_df$Var)
model_coeffs_df$Var <- round(model_coeffs_df$Var,4)

mixed_effects3 <- merge(mixed_effects2, model_coeffs_df, by = "Nutrient")
mixed_effects3$Singularity <- ifelse(mixed_effects3$Singularity == "FALSE", "not singular", "singular")

mixed_effects3$Nutrient <- gsub("\\[", "(", mixed_effects3$Nutrient)
mixed_effects3$Nutrient <- gsub("\\]", ")", mixed_effects3$Nutrient)
mixed_effects3$Nutrient <- gsub("OM", "SOM", mixed_effects3$Nutrient)
  
mixed_effects3$facet_label <- paste0(
  mixed_effects3$Nutrient, " (Var: ", mixed_effects3$Var, ", ", mixed_effects3$Singularity, ")"
)

plot2 =ggplot(mixed_effects3, 
  aes(y=Variable, x=bootMed, fill=pval)) +
  geom_pointrange(shape=21, size=3, aes(xmax=upper, xmin= lower)) +
  facet_wrap(~facet_label, scales="fixed", ncol=1) +
  scale_fill_manual(values = c("#f1a340","#f7f7f7"), name="p-value") +
  theme_bw() +
  ylab("") +
  xlab("LMM: β1-Coef.± 95%CI") +
  theme(strip.background=element_rect(fill="white",colour="black")) +
  theme(strip.text=element_text(size=25,colour="black")) +
  
  theme(axis.text.y=element_text(size=25,colour="black")) +
  theme(axis.text.x=element_text(size=25,colour="black")) +
  theme(axis.title.x=element_text(size=25,colour="black")) +
  
  theme(legend.text=element_text(size=25,colour="black")) + 
  theme(legend.title=element_text(size=25,colour="black")) + 
  theme(legend.position="top",axis.title.y=element_text(size=25,colour="black")) + 
  theme(legend.key.size=unit(2,"cm")) +
  theme(legend.text=element_markdown()) +
  
  geom_vline(xintercept=0, linetype=2) +
  xlim(-2, 2)

```

Save the image
```{r}
png(filename = "Fig1_SoilLab_revised.png",
    width = 8000, 
    height = 3000, 
    res=300)
print(ggarrange(plot1, plot2,
                labels = c("A)","B)"),
                font.label = list(size = 24)))
dev.off()

```
Create q-q-plots for total nitrogen and SOM 
```{r}

data_TN <- nutrients4 %>% filter(Nutrient_label=='paste("N (%)")') %>% pull(Variable) 
data_SOM <- nutrients4 %>% filter(Nutrient_label=='paste("SOM (%)")') %>% pull(Variable) 

png("QQ_Plots.png", width = 1200, height = 600)

  par(mfrow = c(1, 2))
  
  qqnorm(data_TN, main = "Q-Q Plot for N (%)")
  qqline(data_TN, col = "red")
  
  qqnorm(data_SOM, main = "Q-Q Plot for SOM (%)")
  qqline(data_SOM, col = "red")

dev.off()
```
Save the rest of the data as SI table.
```{r}
write.csv(file = file.path("../OutputData", "TableS2_SoilLab.csv"), filter(mixed_effects, Variable!="(Intercept)"))
```

```{r}
print(paste0("The end!!!"))
```