```{r}
library(dplyr)
library(tidyr)
library(lme4)
library(tidyverse)
library(ggpubr)
library(ggtext)
library(reshape2)
```

Load the soil data
```{r}
soil_lab = read.csv(file.path("../InputData", "soil_lab.csv"), check.names=F)
soil_lab_reduced = soil_lab[, c("Experimental_Year", "Block", "Tillage", "Fertilization", "OM[%]","N[%]")]
soil_lab_reduced <- soil_lab_reduced %>% dplyr::rename(Year = Experimental_Year)
soil_lab_reduced <- soil_lab_reduced %>%
  mutate(Block = case_when(
    Year == 2019 & Block == "A1" ~ "1",
    Year == 2019 & Block == "A3" ~ "2",
    Year == 2019 & Block == "B1" ~ "3",
    Year == 2019 & Block == "B3" ~ "4",
    TRUE ~ Block 
  ))

soil_lab_reduced <- soil_lab_reduced %>%
  mutate(Block = case_when(
    Block == "A2" ~ "1",
    Block == "A3" ~ "2",
    Block == "B1" ~ "3",
    Block == "B2" ~ "4",
    TRUE ~ Block
  ))

soil_lab_reduced <- soil_lab_reduced %>%
  mutate(Tillage = dplyr::recode(Tillage, "Plough" = "MP", "Cultivator" = "CT")) %>%
  mutate(Fertilization = dplyr::recode(Fertilization, "extensive" = "Ext", "intensive" = "Int")) %>% 
  dplyr::rename("OM" = "OM[%]")

```

Load the 16S data
```{r}
metadata=read.csv(file.path("../InputData", "metadata1.csv"))%>%na.omit()
#Load the metadata
```

Create the Sequencer metadata based on the sample name
```{r}
GRfiles=read.csv(file.path("../OutputData", "All_Growth_Rates_for_All_mapped_ASVs.csv"))
GRfiles$ASV=GRfiles$V1
GRfiles=dcast(GRfiles,ASV~.,value.var = "DoublingTime", mean)
```
Generate a distribution plot of the growth rates to select the best
division point for slow and fast growing taxa.
```{r}
library(RColorBrewer)
```

```{r}
GRfiles$Trait=GRfiles$.
limit=median((GRfiles$.))
GRfiles$Trait[GRfiles$.>=limit]="slow_grower"
GRfiles$Trait[GRfiles$.<limit]="fast_grower"

```

```{r}
distributionplot= ggplot(GRfiles,aes(x=log10(.))) +
  theme_bw() + 
  geom_density(alpha=0.5, fill="skyblue4") +
  ylab("Density") +
  xlab("Log10 mean mDbTs (hours) for all ASVs mapped to different genomes") +
  
  theme(strip.background=element_rect(fill="white",colour="black")) +
  theme(strip.text=element_text(size=25,colour="black")) +
  
  theme(axis.text.y=element_text(size=25,colour="black")) +
  theme(axis.text.x=element_text(size=25,colour="black")) +
  theme(axis.title.x=element_text(size=25,colour="black")) +
 
  theme(legend.text=element_text(size=25,colour="black")) + 
  theme(legend.title=element_text(size=25,colour="black")) + 
  theme(legend.position="top",axis.title.y=element_text(size=25,colour="black")) + 
  theme(legend.key.size=unit(2,"cm")) +
  
  geom_vline(aes(xintercept=(log10(median(GRfiles$.)))),colour="black",linetype="dashed") 

```



Load the abundances 
```{r,  results="hide"}
ASVtaxonomy=read.csv(file.path("../InputData", "16SMLERarefied_table.csv"),row.names = "X") %>%
  t() %>%
  as.data.frame() %>%
  rownames_to_column(var="ASV")
```
Calculate the ratio of ASVs related to fast and slow growing bacteria in 
every sample
```{r}
ASVtaxonomy_Ratio_RAS=filter(ASVtaxonomy, 
    ASV%in%c(GRfiles$ASV))%>%
  gather(-ASV, key="Sample",value="RA")%>% filter(Sample%in%c(unique(metadata$Sample)))%>%
  
    full_join(metadata) %>%
select(Fertilization=Int, everything()) %>%

full_join(GRfiles)%>%filter(RA!="NA")

ASVtaxonomy_Ratio_RAS$Block=as.character(ASVtaxonomy_Ratio_RAS$Block)

RAS_RH_Ratio_data16S <- full_join(soil_lab_reduced, ASVtaxonomy_Ratio_RAS, 
                         by = c("Year", "Tillage", "Fertilization", "Block"))%>%
  filter(RA!="NA")
RAS_RH_Ratio_data16S2=dcast(RAS_RH_Ratio_data16S, 
OM+Sample+Tillage+Fertilization+Year+Soil_Type~Trait,
value.var = "RA",sum)

RAS_RH_Ratio_data16S2$Ratio=((
RAS_RH_Ratio_data16S2$fast_grower+1)/(RAS_RH_Ratio_data16S2$slow_grower+1))
RAS_RH_Ratio_data16S2$Soil_Type[RAS_RH_Ratio_data16S2$Soil_Type=="RAS"]="BS"
```
Ratios
```{r}
RAS_RH_Ratio_data16S2$G=paste0(RAS_RH_Ratio_data16S2$Soil_Type,RAS_RH_Ratio_data16S2$Tillage)
dunns= dunn.test::dunn.test(RAS_RH_Ratio_data16S2$Ratio, RAS_RH_Ratio_data16S2$G, method = "BH")
comparisons=data.frame(comparisons=dunns$comparisons, p=dunns$P.adjusted)%>%
  separate(., "comparisons", into = c("row","col"), sep = " - ")
orderlist= aggregate( RAS_RH_Ratio_data16S2, Ratio~G, mean)
comparisons=full_join(comparisons, orderlist%>%mutate(row=G), by="row")%>%
  na.omit()
comparisons=comparisons[order(comparisons$Ratio, decreasing = T),]
names1=paste0(comparisons$row,"-", comparisons$col)
p=comparisons$p
names(p)=names1
letters=  multcompView::multcompLetters(p,  
compare = "<", reversed =F)$Letters%>%as.data.frame()
colnames(letters)="L1"
letters$G=rownames(letters)
RAS_RH_Ratio_data16S3=full_join(RAS_RH_Ratio_data16S2,letters)
RAS_RH_Ratio_data16S3$equal=" "
plotdiff=
ggplot(RAS_RH_Ratio_data16S3, 
  aes(x=Soil_Type, y=Ratio,  fill= paste(Tillage))) +
  geom_jitter(shape=21, size=2, position = position_jitterdodge(jitter.width =0.25,dodge.width = 1)) +
  geom_boxplot(alpha=0.5, position = position_dodge(width = 1)) +
  
  scale_fill_brewer(name="",palette = "Dark2") +
  theme_bw() +
  xlab("") +
  ylab("RA ratio of pred. fast/slow-growing bacterial ASVs") +
  theme(strip.background=element_rect(fill="white",colour="white")) +
  theme(strip.text=element_text(size=25,colour="black",angle = 0)) +
  
  theme(axis.text.x=element_text(size=25,colour="black")) +
  theme(axis.title.x=element_text(size=25,colour="black")) +
  
  theme(legend.text=element_text(size=25,colour="black")) + 
  theme(legend.title=element_text(size=25,colour="black")) + 
  theme(legend.position="top",
        axis.text.y=element_text(size=25,colour="black"),
        axis.title.y=element_text(size=25,colour="black")) + 
  theme(legend.key.size=unit(2,"cm")) +
    geom_text(stat = "summary", 
aes(y=Ratio+0.5, label=L1), size=9, position = position_dodge(width = 1)) +
theme(legend.position = "right")+facet_wrap(~equal)


```

```{r}
RAS_RH_Ratio_data16S_BS=filter(RAS_RH_Ratio_data16S2, Soil_Type=="BS")
RAS_RH_Ratio_data16S_BS_rho=cor.test(RAS_RH_Ratio_data16S_BS$OM,RAS_RH_Ratio_data16S_BS$Ratio, method = "spearman")
RAS_RH_Ratio_data16S_RH=filter(RAS_RH_Ratio_data16S2, Soil_Type=="RH")
RAS_RH_Ratio_data16S_RH_rho=cor.test(RAS_RH_Ratio_data16S_RH$OM,RAS_RH_Ratio_data16S_RH$Ratio, method = "spearman")
correlations1=data.frame(Soil_Type=c("BS","RH"),
rho=c(round(RAS_RH_Ratio_data16S_BS_rho$estimate,2),
round(RAS_RH_Ratio_data16S_RH_rho$estimate,2)),
p_values=c(round(RAS_RH_Ratio_data16S_BS_rho$p.value,4),
round(RAS_RH_Ratio_data16S_RH_rho$p.value,4)))
write.csv(correlations1,file ="../OutputData/SOM_RATIO_Slow_Fast_growers_Total_Spearman_rho.csv")
plotcor=
ggplot(RAS_RH_Ratio_data16S2, 
  aes(x=OM, y=Ratio,  fill= paste(Tillage))) +
  geom_point(shape=21, size=2) +
  geom_smooth(method = "lm")+
  scale_fill_brewer(name="",palette = "Dark2") +
  theme_bw() +
  xlab("SOM") +
  ylab("RA ratio of pred. fast/slow-growing bacterial ASVs") +
  theme(strip.background=element_rect(fill="white",colour="white")) +
  theme(strip.text=element_text(size=25,colour="black",angle = 0)) +
  
  theme(axis.text.x=element_text(size=25,colour="black")) +
  theme(axis.title.x=element_text(size=25,colour="black")) +
  
  theme(legend.text=element_text(size=25,colour="black")) + 
  theme(legend.title=element_text(size=25,colour="black")) + 
  theme(legend.position="right",
        axis.text.y=element_text(size=25,colour="black"),
        axis.title.y=element_text(size=25,colour="black")) + 
  theme(legend.key.size=unit(2,"cm")) +stat_cor(method = "spearman", aes(colour = Tillage),size=7.5, cor.coef.name="ρ")+
  scale_color_brewer(palette = "Dark2", name="")+
  facet_wrap(~Soil_Type, nrow=2)
plots1=ggarrange(plotdiff,plotcor, common.legend = T, nrow= 1, legend = "right", labels = c("A)","B)"),font.label = list(size=20))

```



```{r}
png(filename="Figure6.png",
      height = 3000,
      width = 4000, 
      res=250
    )
print(plots1)
dev.off()
```

The end!!! Part1
Additional testing for genome size and 



```{r}
genome_size=read.delim("../InputData/genomesizecheckM2.tsv")%>%
  select(Genome=Name, Genome_Size,Completeness, Contamination)%>%
  mutate(genome=str_replace(Genome,"_G.*", ""))%>%
    select(genome, Genome_Size,Completeness, Contamination)
genome_size$Genome_Size2=genome_size$Genome_Size+
  (1-genome_size$Completeness/100)*genome_size$Genome_Size-
  (genome_size$Contamination/100)*genome_size$Genome_Size

matches= read.delim(file =  "../16S_ASVdada2/ASV_GTDB.mapped_global.txt", header = F)
matches$codname=gsub(" d_*.*","", matches$V2)

matches$genome=paste0( gsub("RS_","", gsub("GB_","", matches$codname)))

matches2=full_join(genome_size, matches)%>%
  filter(Genome_Size2!="NA")

GSfiles=dcast(matches2,V1~.,value.var = "Genome_Size2", mean)%>%
  select(ASV=V1,Genome_Size=".")
```

```{r}
GSfiles$Trait=GSfiles$Genome_Size
limit=median((GSfiles$Genome_Size))
GSfiles$Trait[GSfiles$Genome_Size>=limit]="Above_Median_Genome_size"
GSfiles$Trait[GSfiles$Genome_Size<limit]="Below_Median_Genome_size"

```



Calculate the ratio of ASVs related to size growing bacteria in 
every sample
```{r}
ASVtaxonomy_Ratio_RAS=filter(ASVtaxonomy, 
    ASV%in%c(GSfiles$ASV))%>%
  gather(-ASV, key="Sample",value="RA")%>% filter(Sample%in%c(unique(metadata$Sample)))%>%
  
    full_join(metadata) %>%
select(Fertilization=Int, everything()) %>%

full_join(GSfiles, by="ASV")%>%filter(RA!="NA")

ASVtaxonomy_Ratio_RAS$Block=as.character(ASVtaxonomy_Ratio_RAS$Block)

RAS_RH_Ratio_data16S <- full_join(soil_lab_reduced, ASVtaxonomy_Ratio_RAS, 
                         by = c("Year", "Tillage", "Fertilization", "Block"))%>%
  filter(RA!="NA")
RAS_RH_Ratio_data16S2=dcast(RAS_RH_Ratio_data16S, 
OM+Sample+Tillage+Fertilization+Year+Soil_Type~Trait,
value.var = "RA",sum)

RAS_RH_Ratio_data16S2$Ratio=((
RAS_RH_Ratio_data16S2$Above_Median_Genome_size+1)/(RAS_RH_Ratio_data16S2$Below_Median_Genome_size+1))
RAS_RH_Ratio_data16S2$Soil_Type[RAS_RH_Ratio_data16S2$Soil_Type=="RAS"]="BS"
```
Ratios
```{r}
RAS_RH_Ratio_data16S2$G=paste0(RAS_RH_Ratio_data16S2$Soil_Type,RAS_RH_Ratio_data16S2$Tillage)
dunns= dunn.test::dunn.test(RAS_RH_Ratio_data16S2$Ratio, RAS_RH_Ratio_data16S2$G, method = "BH")
comparisons=data.frame(comparisons=dunns$comparisons, p=dunns$P.adjusted)%>%
  separate(., "comparisons", into = c("row","col"), sep = " - ")
orderlist= aggregate( RAS_RH_Ratio_data16S2, Ratio~G, mean)
comparisons=full_join(comparisons, orderlist%>%mutate(row=G), by="row")%>%
  na.omit()
comparisons=comparisons[order(comparisons$Ratio, decreasing = T),]
names1=paste0(comparisons$row,"-", comparisons$col)
p=comparisons$p
names(p)=names1
letters=  multcompView::multcompLetters(p,  
compare = "<", reversed =F)$Letters%>%as.data.frame()
colnames(letters)="L1"
letters$G=rownames(letters)
RAS_RH_Ratio_data16S3=full_join(RAS_RH_Ratio_data16S2,letters)
RAS_RH_Ratio_data16S3$equal=" "
plotdiff=
ggplot(RAS_RH_Ratio_data16S3, 
  aes(x=Soil_Type, y=Ratio,  fill= paste(Tillage))) +
  geom_jitter(shape=21, size=2, position = position_jitterdodge(jitter.width =0.25,dodge.width = 1)) +
  geom_boxplot(alpha=0.5, position = position_dodge(width = 1)) +
  
  scale_fill_brewer(name="",palette = "Dark2") +
  theme_bw() +
  xlab("") +
  ylab("RA ratio: ASVs with above/below average pred. genome sizes") +
  theme(strip.background=element_rect(fill="white",colour="white")) +
  theme(strip.text=element_text(size=25,colour="black",angle = 0)) +
  
  theme(axis.text.x=element_text(size=25,colour="black")) +
  theme(axis.title.x=element_text(size=25,colour="black")) +
  
  theme(legend.text=element_text(size=25,colour="black")) + 
  theme(legend.title=element_text(size=25,colour="black")) + 
  theme(legend.position="top",
        axis.text.y=element_text(size=25,colour="black"),
        axis.title.y=element_text(size=25,colour="black")) + 
  theme(legend.key.size=unit(2,"cm")) +
    geom_text(stat = "summary", 
aes(y=Ratio+0.5, label=L1), size=9, position = position_dodge(width = 1)) +
theme(legend.position = "right")+facet_wrap(~equal)


```

```{r}
plotcor=
ggplot(RAS_RH_Ratio_data16S2, 
  aes(x=OM, y=Ratio,  fill= paste(Tillage))) +
  geom_point(shape=21, size=2) +
  geom_smooth(method = "lm")+
  scale_fill_brewer(name="",palette = "Dark2") +
  theme_bw() +
  xlab("SOM") +
  ylab("RA ratio: ASVs with above/below average pred. genome sizes") +
  theme(strip.background=element_rect(fill="white",colour="white")) +
  theme(strip.text=element_text(size=25,colour="black",angle = 0)) +
  
  theme(axis.text.x=element_text(size=25,colour="black")) +
  theme(axis.title.x=element_text(size=25,colour="black")) +
  
  theme(legend.text=element_text(size=25,colour="black")) + 
  theme(legend.title=element_text(size=25,colour="black")) + 
  theme(legend.position="right",
        axis.text.y=element_text(size=25,colour="black"),
        axis.title.y=element_text(size=25,colour="black")) + 
  theme(legend.key.size=unit(2,"cm")) +stat_cor(method = "spearman", aes(colour = Tillage),size=7.5, cor.coef.name="ρ")+
  scale_color_brewer(palette = "Dark2", name="")+
  facet_wrap(~Soil_Type, nrow=2)
plots2=ggarrange(plotdiff,plotcor, common.legend = T, nrow= 1, legend = "right", labels = c("A)","B)"),font.label = list(size=20))
```

```{r}

dir.create(file.path("../FigS8_Genome_size_ASV_Ratios"), showWarnings = FALSE)
png(filename = file.path("../FigS8_Genome_size_ASV_Ratios",
                         "FigS8_Genome_size_ASV_Ratios.png"),
      height = 3000,
      width = 4000, 
      res=250
    )
print(plots2)
dev.off()
```

````{r}
path="../../all_dbcan_files"
list1=list.files(path, pattern="*txt", recursive = TRUE)
all_dbcans=function(x) {
path_to_genome <- paste0(path, "/",list1[x])
#if (file.info(path_to_genome)$size>0){ works only in linux
if ( !is.na (file.info(path_to_genome)$size)&& file.info(path_to_genome)$size > 0){ #works  in windows

file1=read.delim(path_to_genome, header = F)
file2=data.frame(G1=paste0(list1[x]), CazymeGenes=nrow(file1))}else{
  file2=data.frame(G1=paste0(list1[x]), CazymeGenes=0)
}
return(file2)
}

resultscazy <- lapply( 1:length(list1), 
                         function(x) all_dbcans(x))

results2cazy=do.call("rbind",resultscazy)%>%
  separate(., col=G1, into=c("Genome","PR"),
sep="_prokka")%>%
  mutate(genome=str_replace(Genome,"_G.*", ""))%>%
    select(genome, CazymeGenes)

results2cazy$genome=gsub("*.*GC","GC",results2cazy$genome
)
matches_cazy=full_join(results2cazy, matches)%>%
  filter(CazymeGenes!="NA")
Cazyfiles=dcast(matches_cazy,V1~.,value.var = "CazymeGenes", mean)%>%
  select(ASV=V1,CazymeGenes=".")


````


```{r}
Cazyfiles$Trait=Cazyfiles$CazymeGenes
limit=median((Cazyfiles$CazymeGenes))
Cazyfiles$Trait[Cazyfiles$CazymeGenes>=limit]="Above_Median_Cazy_Genes"
Cazyfiles$Trait[Cazyfiles$CazymeGenes<limit]="Below_Median_Cazy_Genes"

```






Calculate the ratio of ASVs related to size growing bacteria in 
every sample
```{r}
ASVtaxonomy_Ratio_RAS=filter(ASVtaxonomy, 
    ASV%in%c(Cazyfiles$ASV))%>%
  gather(-ASV, key="Sample",value="RA")%>% filter(Sample%in%c(unique(metadata$Sample)))%>%
  
    full_join(metadata) %>%
select(Fertilization=Int, everything()) %>%

full_join(Cazyfiles, by="ASV")%>%filter(RA!="NA")

ASVtaxonomy_Ratio_RAS$Block=as.character(ASVtaxonomy_Ratio_RAS$Block)

RAS_RH_Ratio_data16S <- full_join(soil_lab_reduced, ASVtaxonomy_Ratio_RAS, 
                         by = c("Year", "Tillage", "Fertilization", "Block"))%>%
  filter(RA!="NA")
RAS_RH_Ratio_data16S2=dcast(RAS_RH_Ratio_data16S, 
OM+Sample+Tillage+Fertilization+Year+Soil_Type~Trait,
value.var = "RA",sum)

RAS_RH_Ratio_data16S2$Ratio=((
RAS_RH_Ratio_data16S2$Above_Median_Cazy_Genes+1)/(RAS_RH_Ratio_data16S2$Below_Median_Cazy_Genes+1))
RAS_RH_Ratio_data16S2$Soil_Type[RAS_RH_Ratio_data16S2$Soil_Type=="RAS"]="BS"
```
Ratios
```{r}
RAS_RH_Ratio_data16S2$G=paste0(RAS_RH_Ratio_data16S2$Soil_Type,RAS_RH_Ratio_data16S2$Tillage)
dunns= dunn.test::dunn.test(RAS_RH_Ratio_data16S2$Ratio, RAS_RH_Ratio_data16S2$G, method = "BH")
comparisons=data.frame(comparisons=dunns$comparisons, p=dunns$P.adjusted)%>%
  separate(., "comparisons", into = c("row","col"), sep = " - ")
orderlist= aggregate( RAS_RH_Ratio_data16S2, Ratio~G, mean)
comparisons=full_join(comparisons, orderlist%>%mutate(row=G), by="row")%>%
  na.omit()
comparisons=comparisons[order(comparisons$Ratio, decreasing = T),]
names1=paste0(comparisons$row,"-", comparisons$col)
p=comparisons$p
names(p)=names1
letters=  multcompView::multcompLetters(p,  
compare = "<", reversed =F)$Letters%>%as.data.frame()
colnames(letters)="L1"
letters$G=rownames(letters)
RAS_RH_Ratio_data16S3=full_join(RAS_RH_Ratio_data16S2,letters)
RAS_RH_Ratio_data16S3$equal=" "
plotdiff=
ggplot(RAS_RH_Ratio_data16S3, 
  aes(x=Soil_Type, y=Ratio,  fill= paste(Tillage))) +
  geom_jitter(shape=21, size=2, position = position_jitterdodge(jitter.width =0.25,dodge.width = 1)) +
  geom_boxplot(alpha=0.5, position = position_dodge(width = 1)) +
  
  scale_fill_brewer(name="",palette = "Dark2") +
  theme_bw() +
  xlab("") +
  ylab("RA ratio: ASV high/low pred. aptitude for carb. metabolism") +
  theme(strip.background=element_rect(fill="white",colour="white")) +
  theme(strip.text=element_text(size=25,colour="black",angle = 0)) +
  
  theme(axis.text.x=element_text(size=25,colour="black")) +
  theme(axis.title.x=element_text(size=25,colour="black")) +
  
  theme(legend.text=element_text(size=25,colour="black")) + 
  theme(legend.title=element_text(size=25,colour="black")) + 
  theme(legend.position="top",
        axis.text.y=element_text(size=25,colour="black"),
        axis.title.y=element_text(size=25,colour="black")) + 
  theme(legend.key.size=unit(2,"cm")) +
    geom_text(stat = "summary", 
aes(y=Ratio+0.5, label=L1), size=9, position = position_dodge(width = 1)) +
theme(legend.position = "right")+facet_wrap(~equal)


```

```{r}
plotcor=
ggplot(RAS_RH_Ratio_data16S2, 
  aes(x=OM, y=Ratio,  fill= paste(Tillage))) +
  geom_point(shape=21, size=2) +
  geom_smooth(method = "lm")+
  scale_fill_brewer(name="",palette = "Dark2") +
  theme_bw() +
  xlab("SOM") +
  ylab("RA ratio: ASV high/low pred. aptitude for carb. metabolism") +
  theme(strip.background=element_rect(fill="white",colour="white")) +
  theme(strip.text=element_text(size=25,colour="black",angle = 0)) +
  
  theme(axis.text.x=element_text(size=25,colour="black")) +
  theme(axis.title.x=element_text(size=25,colour="black")) +
  
  theme(legend.text=element_text(size=25,colour="black")) + 
  theme(legend.title=element_text(size=25,colour="black")) + 
  theme(legend.position="right",
        axis.text.y=element_text(size=25,colour="black"),
        axis.title.y=element_text(size=25,colour="black")) + 
  theme(legend.key.size=unit(2,"cm")) +stat_cor(method = "spearman", aes(colour = Tillage),size=7.5, cor.coef.name="ρ")+
  scale_color_brewer(palette = "Dark2", name="")+
  facet_wrap(~Soil_Type, nrow=2)
plots3=ggarrange(plotdiff,plotcor, common.legend = T, nrow= 1, legend = "right", labels = c("A)","B)"),font.label = list(size=20))
```

```{r}

dir.create(file.path("../FigS9_Cazyme_genes_ASV_Ratios"), showWarnings = FALSE)
png(filename = file.path("../FigS9_Cazyme_genes_ASV_Ratios",
                         "FigS9__Cazyme_genes_ASV_Ratios.png"),
      height = 3000,
      width = 4000, 
      res=250
    )
print(plots3)
dev.off()
```

```{r}
distributionplot1= ggplot(GRfiles,aes(x=log10(.))) +
  theme_bw() + 
  geom_density(alpha=0.5, fill="skyblue4") +
  ylab("Density") +
  xlab("Log10 mean mDbTs (hours) for all ASVs based on the mapping to closely related genomes") +
  
  theme(strip.background=element_rect(fill="white",colour="black")) +
  theme(strip.text=element_text(size=25,colour="black")) +
  
  theme(axis.text.y=element_text(size=25,colour="black")) +
  theme(axis.text.x=element_text(size=25,colour="black")) +
  theme(axis.title.x=element_text(size=25,colour="black")) +
 
  theme(legend.text=element_text(size=25,colour="black")) + 
  theme(legend.title=element_text(size=25,colour="black")) + 
  theme(legend.position="top",axis.title.y=element_text(size=25,colour="black")) + 
  theme(legend.key.size=unit(2,"cm")) +
  
  geom_vline(aes(xintercept=(log10(median(GRfiles$.)))),colour="black",linetype="dashed") 

distributionplot2= ggplot(GSfiles,aes(x=log10(Genome_Size))) +
  theme_bw() + 
  geom_density(alpha=0.5, fill="skyblue4") +
  ylab("Density") +
  xlab("Pred. Genome size (log10 bp) for all ASVs based to the mapping on closely related genomes") +
  
  theme(strip.background=element_rect(fill="white",colour="black")) +
  theme(strip.text=element_text(size=25,colour="black")) +
  
  theme(axis.text.y=element_text(size=25,colour="black")) +
  theme(axis.text.x=element_text(size=25,colour="black")) +
  theme(axis.title.x=element_text(size=25,colour="black")) +
 
  theme(legend.text=element_text(size=25,colour="black")) + 
  theme(legend.title=element_text(size=25,colour="black")) + 
  theme(legend.position="top",axis.title.y=element_text(size=25,colour="black")) + 
  theme(legend.key.size=unit(2,"cm")) +
  
  geom_vline(aes(xintercept=(log10(median(GSfiles$Genome_Size)))),colour="black",linetype="dashed") 


distributionplot3= ggplot(Cazyfiles,aes(x=log10(CazymeGenes+1))) +
  theme_bw() + 
  geom_density(alpha=0.5, fill="skyblue4") +
  ylab("Density") +
  xlab("log10 Number of pred. average. CAZyme genes for all ASVs based on the mapping to closely related genomes") +
  
  theme(strip.background=element_rect(fill="white",colour="black")) +
  theme(strip.text=element_text(size=25,colour="black")) +
  
  theme(axis.text.y=element_text(size=25,colour="black")) +
  theme(axis.text.x=element_text(size=25,colour="black")) +
  theme(axis.title.x=element_text(size=25,colour="black")) +
 
  theme(legend.text=element_text(size=25,colour="black")) + 
  theme(legend.title=element_text(size=25,colour="black")) + 
  theme(legend.position="top",axis.title.y=element_text(size=25,colour="black")) + 
  theme(legend.key.size=unit(2,"cm")) +
  
  geom_vline(aes(xintercept=(log10(median(Cazyfiles$CazymeGenes+1)))),colour="black",linetype="dashed") 

plots4=ggarrange(distributionplot1,distributionplot2,distributionplot3, labels = c("A)","B)","C)"),ncol=1)
```

```{r}

dir.create(file.path("../FigS7_Distribution_Plots_ASV_Ratios"), showWarnings = FALSE)
png(filename = file.path("../FigS7_Distribution_Plots_ASV_Ratios",
                         "FigS7_Distribution_Plots_ASV_Ratios.png"),
      height = 3000,
      width = 5000, 
      res=250
    )
print(plots4)
dev.off()
```





````{r}
print("The full End!!")
````
