```{r}
library(dplyr)
library(tidyr)
library(lme4)
library(tidyverse)
library(ggpubr)
library(ggtext)
library(reshape2)
```

Load the soil data
```{r}
soil_lab = read.csv(file.path("../InputData", "soil_lab.csv"), check.names=F)
soil_lab_reduced = soil_lab[, c("Experimental_Year", "Block", "Tillage", "Fertilization", "OM[%]","N[%]")]
soil_lab_reduced <- soil_lab_reduced %>% dplyr::rename(Year = Experimental_Year)
soil_lab_reduced <- soil_lab_reduced %>%
  mutate(Block = case_when(
    Year == 2019 & Block == "A1" ~ "1",
    Year == 2019 & Block == "A3" ~ "2",
    Year == 2019 & Block == "B1" ~ "3",
    Year == 2019 & Block == "B3" ~ "4",
    TRUE ~ Block 
  ))

soil_lab_reduced <- soil_lab_reduced %>%
  mutate(Block = case_when(
    Block == "A2" ~ "1",
    Block == "A3" ~ "2",
    Block == "B1" ~ "3",
    Block == "B2" ~ "4",
    TRUE ~ Block
  ))

soil_lab_reduced <- soil_lab_reduced %>%
  mutate(Tillage = dplyr::recode(Tillage, "Plough" = "MP", "Cultivator" = "CT")) %>%
  mutate(Fertilization = dplyr::recode(Fertilization, "extensive" = "Ext", "intensive" = "Int")) %>% 
  dplyr::rename("OM" = "OM[%]")

```

Load the 16S data
```{r}
metadata=read.csv(file.path("../InputData", "metadata1.csv"))%>%na.omit()
#Load the metadata
```

Create the Sequencer metadata based on the sample name
```{r}
GRfiles=read.csv(file.path("../OutputData", "All_Growth_Rates_for_All_mapped_ASVs.csv"))
GRfiles$ASV=GRfiles$V1
GRfiles=dcast(GRfiles,ASV~.,value.var = "DoublingTime", mean)
```
Generate a distribution plot of the growth rates to select the best
division point for slow and fast growing taxa.
```{r}
library(RColorBrewer)
```

```{r}
GRfiles$Trait=GRfiles$.
limit=median((GRfiles$.))
GRfiles$Trait[GRfiles$.>=limit]="slow_grower"
GRfiles$Trait[GRfiles$.<limit]="fast_grower"

```

```{r}
distributionplot= ggplot(GRfiles,aes(x=log10(.))) +
  theme_bw() + 
  geom_density(alpha=0.5, fill="skyblue4") +
  ylab("Density") +
  xlab("Log10 mean mDbTs (hours) for all ASVs mapped to different genomes") +
  
  theme(strip.background=element_rect(fill="white",colour="black")) +
  theme(strip.text=element_text(size=25,colour="black")) +
  
  theme(axis.text.y=element_text(size=25,colour="black")) +
  theme(axis.text.x=element_text(size=25,colour="black")) +
  theme(axis.title.x=element_text(size=25,colour="black")) +
 
  theme(legend.text=element_text(size=25,colour="black")) + 
  theme(legend.title=element_text(size=25,colour="black")) + 
  theme(legend.position="top",axis.title.y=element_text(size=25,colour="black")) + 
  theme(legend.key.size=unit(2,"cm")) +
  
  geom_vline(aes(xintercept=(log10(median(GRfiles$.)))),colour="black",linetype="dashed") 

```



Load the abundances 
```{r,  results="hide"}
ASVtaxonomy=read.csv(file.path("../InputData", "16SMLERarefied_table.csv"),row.names = "X") %>%
  t() %>%
  as.data.frame() %>%
  rownames_to_column(var="ASV")
```
Calculate the ratio of ASVs related to fast and slow growing bacteria in 
every sample
```{r}
ASVtaxonomy_Ratio_RAS=filter(ASVtaxonomy, 
    ASV%in%c(GRfiles$ASV))%>%
  gather(-ASV, key="Sample",value="RA")%>% filter(Sample%in%c(unique(metadata$Sample)))%>%
  
    full_join(metadata) %>%
select(Fertilization=Int, everything()) %>%

full_join(GRfiles)%>%filter(RA!="NA")

ASVtaxonomy_Ratio_RAS$Block=as.character(ASVtaxonomy_Ratio_RAS$Block)

RAS_RH_Ratio_data16S <- full_join(soil_lab_reduced, ASVtaxonomy_Ratio_RAS, 
                         by = c("Year", "Tillage", "Fertilization", "Block"))%>%
  filter(RA!="NA")
RAS_RH_Ratio_data16S2=dcast(RAS_RH_Ratio_data16S, 
OM+Sample+Tillage+Fertilization+Year+Soil_Type~Trait,
value.var = "RA",sum)

RAS_RH_Ratio_data16S2$Ratio=((
RAS_RH_Ratio_data16S2$fast_grower+1)/(RAS_RH_Ratio_data16S2$slow_grower+1))
RAS_RH_Ratio_data16S2$Soil_Type[RAS_RH_Ratio_data16S2$Soil_Type=="RAS"]="BS"
```
Ratios
```{r}
RAS_RH_Ratio_data16S2$G=paste0(RAS_RH_Ratio_data16S2$Soil_Type,RAS_RH_Ratio_data16S2$Tillage)
dunns= dunn.test::dunn.test(RAS_RH_Ratio_data16S2$Ratio, RAS_RH_Ratio_data16S2$G, method = "BH")
comparisons=data.frame(comparisons=dunns$comparisons, p=dunns$P.adjusted)%>%
  separate(., "comparisons", into = c("row","col"), sep = " - ")
orderlist= aggregate( RAS_RH_Ratio_data16S2, Ratio~G, mean)
comparisons=full_join(comparisons, orderlist%>%mutate(row=G), by="row")%>%
  na.omit()
comparisons=comparisons[order(comparisons$Ratio, decreasing = T),]
names1=paste0(comparisons$row,"-", comparisons$col)
p=comparisons$p
names(p)=names1
letters=  multcompView::multcompLetters(p,  
compare = "<", reversed =F)$Letters%>%as.data.frame()
colnames(letters)="L1"
letters$G=rownames(letters)
RAS_RH_Ratio_data16S3=full_join(RAS_RH_Ratio_data16S2,letters)
RAS_RH_Ratio_data16S3$equal=" "
plotdiff=
ggplot(RAS_RH_Ratio_data16S3, 
  aes(x=Soil_Type, y=Ratio,  fill= paste(Tillage))) +
  geom_jitter(shape=21, size=2, position = position_jitterdodge(jitter.width =0.25,dodge.width = 1)) +
  geom_boxplot(alpha=0.5, position = position_dodge(width = 1)) +
  
  scale_fill_brewer(name="",palette = "Dark2") +
  theme_bw() +
  xlab("") +
  ylab("RA ratio of fast/slow-growing bacterial ASVs") +
  theme(strip.background=element_rect(fill="white",colour="white")) +
  theme(strip.text=element_text(size=25,colour="black",angle = 0)) +
  
  theme(axis.text.x=element_text(size=25,colour="black")) +
  theme(axis.title.x=element_text(size=25,colour="black")) +
  
  theme(legend.text=element_text(size=25,colour="black")) + 
  theme(legend.title=element_text(size=25,colour="black")) + 
  theme(legend.position="top",
        axis.text.y=element_text(size=25,colour="black"),
        axis.title.y=element_text(size=25,colour="black")) + 
  theme(legend.key.size=unit(2,"cm")) +
    geom_text(stat = "summary", 
aes(y=Ratio+0.5, label=L1), size=9, position = position_dodge(width = 1)) +
theme(legend.position = "right")+facet_wrap(~equal)


```

```{r}
plotcor=
ggplot(RAS_RH_Ratio_data16S2, 
  aes(x=OM, y=Ratio,  fill= paste(Tillage))) +
  geom_point(shape=21, size=2, position = position_jitterdodge(jitter.width =0.25,dodge.width = 1)) +
  geom_smooth(method = "lm")+
  scale_fill_brewer(name="",palette = "Dark2") +
  theme_bw() +
  xlab("SOM") +
  ylab("RA ratio of fast/slow-growing bacterial ASVs") +
  theme(strip.background=element_rect(fill="white",colour="white")) +
  theme(strip.text=element_text(size=25,colour="black",angle = 0)) +
  
  theme(axis.text.x=element_text(size=25,colour="black")) +
  theme(axis.title.x=element_text(size=25,colour="black")) +
  
  theme(legend.text=element_text(size=25,colour="black")) + 
  theme(legend.title=element_text(size=25,colour="black")) + 
  theme(legend.position="right",
        axis.text.y=element_text(size=25,colour="black"),
        axis.title.y=element_text(size=25,colour="black")) + 
  theme(legend.key.size=unit(2,"cm")) +stat_cor(method = "spearman", aes(colour = Tillage),size=7.5, cor.coef.name="ρ")+
  scale_color_brewer(palette = "Dark2", name="")+
  facet_wrap(~Soil_Type, nrow=2)
plots1=ggarrange(plotdiff,plotcor, common.legend = T, nrow= 1, legend = "right")
```

Fast_grower bacterial ASVs
```{r}
RAS_RH_Ratio_data16S2$G=paste0(RAS_RH_Ratio_data16S2$Soil_Type,RAS_RH_Ratio_data16S2$Tillage)
dunns= dunn.test::dunn.test(RAS_RH_Ratio_data16S2$fast_grower, RAS_RH_Ratio_data16S2$G, method = "BH")
comparisons=data.frame(comparisons=dunns$comparisons, p=dunns$P.adjusted)%>%
  separate(., "comparisons", into = c("row","col"), sep = " - ")
orderlist= aggregate( RAS_RH_Ratio_data16S2, fast_grower~G, mean)
comparisons=full_join(comparisons, orderlist%>%mutate(row=G), by="row")%>%
  na.omit()
comparisons=comparisons[order(comparisons$fast_grower, decreasing = T),]
names1=paste0(comparisons$row,"-", comparisons$col)
p=comparisons$p
names(p)=names1
letters=  multcompView::multcompLetters(p,  
compare = "<", reversed =F)$Letters%>%as.data.frame()
colnames(letters)="L1"
letters$G=rownames(letters)
RAS_RH_Ratio_data16S4=full_join(RAS_RH_Ratio_data16S2,letters)
RAS_RH_Ratio_data16S4$equal=" "
plotdiff_fast_growers=
ggplot(RAS_RH_Ratio_data16S4, 
  aes(x=Soil_Type, y=(100*fast_grower/15349),  fill= paste(Tillage))) +
  geom_jitter(shape=21, size=2, position = position_jitterdodge(jitter.width =0.25,dodge.width = 1)) +
  geom_boxplot(alpha=0.5, position = position_dodge(width = 1)) +
  
  scale_fill_brewer(name="",palette = "Dark2") +
  theme_bw() +
  xlab("") +
  ylab("RA[%] of fast-growing bacterial ASVs") +
  theme(strip.background=element_rect(fill="white",colour="white")) +
  theme(strip.text=element_text(size=25,colour="black",angle = 0)) +
  
  theme(axis.text.x=element_text(size=25,colour="black")) +
  theme(axis.title.x=element_text(size=25,colour="black")) +
  
  theme(legend.text=element_text(size=25,colour="black")) + 
  theme(legend.title=element_text(size=25,colour="black")) + 
  theme(legend.position="top",
        axis.text.y=element_text(size=25,colour="black"),
        axis.title.y=element_text(size=25,colour="black")) + 
  theme(legend.key.size=unit(2,"cm")) +
    geom_text(stat = "summary", 
aes(y=(100*fast_grower/15349)+13, label=L1), size=9, position = position_dodge(width = 1)) +
theme(legend.position = "right")+facet_wrap(~equal)
```

```{r}
plotcor_fast_growers=
ggplot(RAS_RH_Ratio_data16S2, 
  aes(x=OM, y=(100*fast_grower/15349),  fill= paste(Tillage))) +
  geom_point(shape=21, size=2, position = position_jitterdodge(jitter.width =0.25,dodge.width = 1)) +
  geom_smooth(method = "lm")+
  scale_fill_brewer(name="",palette = "Dark2") +
  theme_bw() +
  xlab("SOM") +
  ylab("RA[%] of fast-growing bacterial ASVs") +
  theme(strip.background=element_rect(fill="white",colour="white")) +
  theme(strip.text=element_text(size=25,colour="black",angle = 0)) +
  
  theme(axis.text.x=element_text(size=25,colour="black")) +
  theme(axis.title.x=element_text(size=25,colour="black")) +
  
  theme(legend.text=element_text(size=25,colour="black")) + 
  theme(legend.title=element_text(size=25,colour="black")) + 
  theme(legend.position="right",
        axis.text.y=element_text(size=25,colour="black"),
        axis.title.y=element_text(size=25,colour="black")) + 
  theme(legend.key.size=unit(2,"cm")) +stat_cor(method = "spearman", aes(colour = Tillage),size=5, cor.coef.name="ρ", label.x = 2.0)+
  scale_color_brewer(palette = "Dark2", name="")+
  facet_wrap(~Soil_Type, nrow=2)
plots2=ggarrange(plotdiff_fast_growers,plotcor_fast_growers, 
                 common.legend = T, ncol = 2, legend = "right")

```


slow_grower bacterial ASVs
```{r}
RAS_RH_Ratio_data16S2$G=paste0(RAS_RH_Ratio_data16S2$Soil_Type,RAS_RH_Ratio_data16S2$Tillage)
dunns= dunn.test::dunn.test(RAS_RH_Ratio_data16S2$slow_grower, RAS_RH_Ratio_data16S2$G, method = "BH")
comparisons=data.frame(comparisons=dunns$comparisons, p=dunns$P.adjusted)%>%
  separate(., "comparisons", into = c("row","col"), sep = " - ")
orderlist= aggregate( RAS_RH_Ratio_data16S2, slow_grower~G, mean)
comparisons=full_join(comparisons, orderlist%>%mutate(row=G), by="row")%>%
  na.omit()
comparisons=comparisons[order(comparisons$slow_grower, decreasing = T),]
names1=paste0(comparisons$row,"-", comparisons$col)
p=comparisons$p
names(p)=names1
letters=  multcompView::multcompLetters(p,  
compare = "<", reversed =F)$Letters%>%as.data.frame()
colnames(letters)="L1"
letters$G=rownames(letters)
RAS_RH_Ratio_data16S4=full_join(RAS_RH_Ratio_data16S2,letters)
RAS_RH_Ratio_data16S4$equal=" "
plotdiff_slow_growers=
ggplot(RAS_RH_Ratio_data16S4, 
  aes(x=Soil_Type, y=(100*slow_grower/15349),  fill= paste(Tillage))) +
  geom_jitter(shape=21, size=2, position = position_jitterdodge(jitter.width =0.25,dodge.width = 1)) +
  geom_boxplot(alpha=0.5, position = position_dodge(width = 1)) +
  
  scale_fill_brewer(name="",palette = "Dark2") +
  theme_bw() +
  xlab("") +
  ylab(" RA[%] of slow-growing bacterial ASVs") +
  theme(strip.background=element_rect(fill="white",colour="white")) +
  theme(strip.text=element_text(size=25,colour="black",angle = 0)) +
  
  theme(axis.text.x=element_text(size=25,colour="black")) +
  theme(axis.title.x=element_text(size=25,colour="black")) +
  
  theme(legend.text=element_text(size=25,colour="black")) + 
  theme(legend.title=element_text(size=25,colour="black")) + 
  theme(legend.position="top",
        axis.text.y=element_text(size=25,colour="black"),
        axis.title.y=element_text(size=25,colour="black")) + 
  theme(legend.key.size=unit(2,"cm")) +
    geom_text(stat = "summary", 
aes(y=log10(100*slow_grower/15349)+0.3, label=L1), size=9, position = position_dodge(width = 1)) +
theme(legend.position = "right")+facet_wrap(~equal)
```

```{r}
plotcor_slow_growers=
ggplot(RAS_RH_Ratio_data16S2, 
  aes(x=OM, y=(100*slow_grower/15349),  fill= paste(Tillage))) +
  geom_point(shape=21, size=2, position = position_jitterdodge(jitter.width =0.25,dodge.width = 1)) +
  geom_smooth(method = "lm")+
  scale_fill_brewer(name="",palette = "Dark2") +
  theme_bw() +
  xlab("SOM") +
  ylab("RA[%] of slow-growing bacterial ASVs") +
  theme(strip.background=element_rect(fill="white",colour="white")) +
  theme(strip.text=element_text(size=25,colour="black",angle = 0)) +
  
  theme(axis.text.x=element_text(size=25,colour="black")) +
  theme(axis.title.x=element_text(size=25,colour="black")) +
  
  theme(legend.text=element_text(size=25,colour="black")) + 
  theme(legend.title=element_text(size=25,colour="black")) + 
  theme(legend.position="right",
        axis.text.y=element_text(size=25,colour="black"),
        axis.title.y=element_text(size=25,colour="black")) + 
  theme(legend.key.size=unit(2,"cm")) +stat_cor(method = "pearson", aes(colour = Tillage),size=5, cor.coef.name="ρ", label.x = 2.0)+
  scale_color_brewer(palette = "Dark2", name="")+
  facet_wrap(~Soil_Type)
plots3=ggarrange(plotdiff_slow_growers,plotcor_slow_growers, common.legend = T, legend = "top")

```
```{r}
png(filename="Figure6.png",
      height = 2000,
      width = 4000, 
      res=250
    )
print(plots1)
dev.off()
```
```{r}
```