```{r}
library(dplyr)
library(tidyr)
library(lme4)
library(tidyverse)
library(ggpubr)
library(ggtext)
library(car)
```
Load the soil data
```{r}
soil_lab = read.csv(file.path("../InputData", "soil_lab.csv"), check.names=F)
soil_lab_reduced = soil_lab[, c("Experimental_Year", "Block", "Tillage", "Fertilization", "OM[%]")]
soil_lab_reduced <- soil_lab_reduced %>% dplyr::rename(Year = Experimental_Year)
soil_lab_reduced <- soil_lab_reduced %>%
  mutate(Block = case_when(
    Year == 2019 & Block == "A1" ~ "1",
    Year == 2019 & Block == "A3" ~ "2",
    Year == 2019 & Block == "B1" ~ "3",
    Year == 2019 & Block == "B3" ~ "4",
    TRUE ~ Block 
  ))

soil_lab_reduced <- soil_lab_reduced %>%
  mutate(Block = case_when(
    Block == "A2" ~ "1",
    Block == "A3" ~ "2",
    Block == "B1" ~ "3",
    Block == "B2" ~ "4",
    TRUE ~ Block
  ))

soil_lab_reduced <- soil_lab_reduced %>%
  mutate(Tillage = dplyr::recode(Tillage, "Plough" = "MP", "Cultivator" = "CT")) %>%
  mutate(Fertilization = dplyr::recode(Fertilization, "extensive" = "Ext", "intensive" = "Int")) %>% 
  dplyr::rename("OM" = "OM[%]")
```

Load the 16S data
```{r}
metadata=read.csv(file.path("../InputData", "metadata1.csv"))%>%na.omit()
#Load the metadata
metadata$Soil_Type[metadata$Soil_Type=="RAS"]="BS"

```

Read the differential abundances 
```{r,  results="hide"}
ASVtaxonomy=read.csv(file.path("../InputData", "16SMLERarefied_table.csv"),row.names = "X") %>%
  t() %>%
  as.data.frame() %>%
  rownames_to_column(var="ASV")

all_models_diff=read.csv(file.path("../OutputData", "TableS3_RespondersPlot.csv_revised"))

bac_rer_number=unique(colSums(ASVtaxonomy[,-1]))
```

Calculate cumulative relative abundance for CT positive responders for each year in 
root-associated soil
```{r}
all_models_diff_CT_RAS =filter(all_models_diff, 
                                          Soil_Type=="BS"& 
                                          coeff<0)

ASVtaxonomy_CT_RAS=filter(ASVtaxonomy, ASV%in%c(all_models_diff_CT_RAS$ASV))%>%
  select(unique(metadata$Sample))

# Start Year 2019 
ASVtaxonomy_CT_RAS_2019=data.frame(sum=apply(ASVtaxonomy_CT_RAS, 2,function(x) sum(x))) %>%
    rownames_to_column(var="Sample") %>%
    full_join(metadata) %>%
    select(Fertilization=Int, everything()) %>%
    filter(Soil_Type=="BS" & Year == 2019)

ASVtaxonomy_CT_RAS_2019$Block=as.character(ASVtaxonomy_CT_RAS_2019$Block)

RAS_CT_data16S_2019 <- inner_join(soil_lab_reduced, ASVtaxonomy_CT_RAS_2019, 
                         by = c("Year", "Tillage", "Fertilization", "Block"))

# End Year 2019

# Start Year 2020 
ASVtaxonomy_CT_RAS_2020=data.frame(sum=apply(ASVtaxonomy_CT_RAS, 2,function(x) sum(x))) %>%
    rownames_to_column(var="Sample") %>%
    full_join(metadata) %>%
    select(Fertilization=Int, everything()) %>%
    filter(Soil_Type=="BS" & Year == 2020)

ASVtaxonomy_CT_RAS_2020$Block=as.character(ASVtaxonomy_CT_RAS_2020$Block)

RAS_CT_data16S_2020 <- inner_join(soil_lab_reduced, ASVtaxonomy_CT_RAS_2020, 
                         by = c("Year", "Tillage", "Fertilization", "Block"))

# End Year 2020

# Start Year 2021 
ASVtaxonomy_CT_RAS_2021=data.frame(sum=apply(ASVtaxonomy_CT_RAS, 2,function(x) sum(x))) %>%
    rownames_to_column(var="Sample") %>%
    full_join(metadata) %>%
    select(Fertilization=Int, everything()) %>%
    filter(Soil_Type=="BS" & Year == 2021)

ASVtaxonomy_CT_RAS_2021$Block=as.character(ASVtaxonomy_CT_RAS_2021$Block)

RAS_CT_data16S_2021 <- inner_join(soil_lab_reduced, ASVtaxonomy_CT_RAS_2021, 
                         by = c("Year", "Tillage", "Fertilization", "Block"))
# End Year 2021
```

Calculate cumulative relative abundance for MP positive responders for each year in 
root-associated soil
```{r}


all_models_diff_MP_RAS=filter(all_models_diff, 
                                    Soil_Type=="BS" &
                                    coeff>0)

ASVtaxonomy_MP_RAS=filter(ASVtaxonomy, ASV%in%c(all_models_diff_MP_RAS$ASV))%>%
  select(unique(metadata$Sample))

# Start Year 2019 
ASVtaxonomy_MP_RAS_2019=data.frame(sum=apply(ASVtaxonomy_MP_RAS, 2,function(x) sum(x))) %>%
    rownames_to_column(var="Sample") %>%
    full_join(metadata) %>%
    select(Fertilization=Int, everything()) %>%
    filter(Soil_Type=="BS" & Year==2019)

ASVtaxonomy_MP_RAS_2019$Block=as.character(ASVtaxonomy_MP_RAS_2019$Block)

RAS_MP_data16S_2019 <- inner_join(soil_lab_reduced, ASVtaxonomy_MP_RAS_2019, 
                         by = c("Year", "Tillage", "Fertilization", "Block"))

# End Year 2019

# Start Year 2020 
ASVtaxonomy_MP_RAS_2020=data.frame(sum=apply(ASVtaxonomy_MP_RAS, 2,function(x) sum(x))) %>%
    rownames_to_column(var="Sample") %>%
    full_join(metadata) %>%
    select(Fertilization=Int, everything()) %>%
    filter(Soil_Type=="BS" & Year==2020)

ASVtaxonomy_MP_RAS_2020$Block=as.character(ASVtaxonomy_MP_RAS_2020$Block)

RAS_MP_data16S_2020 <- inner_join(soil_lab_reduced, ASVtaxonomy_MP_RAS_2020, 
                         by = c("Year", "Tillage", "Fertilization", "Block"))


# End Year 2020

# Start Year 2021 
ASVtaxonomy_MP_RAS_2021=data.frame(sum=apply(ASVtaxonomy_MP_RAS, 2,function(x) sum(x))) %>%
    rownames_to_column(var="Sample") %>%
    full_join(metadata) %>%
    select(Fertilization=Int, everything()) %>%
    filter(Soil_Type=="BS" & Year == 2021)

ASVtaxonomy_MP_RAS_2021$Block=as.character(ASVtaxonomy_MP_RAS_2021$Block)

RAS_MP_data16S_2021 <- inner_join(soil_lab_reduced, ASVtaxonomy_MP_RAS_2021, 
                         by = c("Year", "Tillage", "Fertilization", "Block"))

# End Year 2021

```
Calculate cumulative relative abundance for CT positive responders for each year in 
rhizosphere
```{r}
all_models_diff_CT_RH=filter(all_models_diff, 
                                        Soil_Type=="RH" &
                                        coeff<0)

ASVtaxonomy_CT_RH=filter(ASVtaxonomy, ASV%in%c(all_models_diff_CT_RH$ASV))%>%
  select(unique(metadata$Sample))


# Start Year 2019 
ASVtaxonomy_CT_RH_2019=data.frame(sum=apply(ASVtaxonomy_CT_RH, 2,function(x) sum(x))) %>%
  rownames_to_column(var="Sample") %>%
  full_join(metadata) %>%
  select(Fertilization=Int, everything()) %>%
  filter(Soil_Type=="RH" & Year==2019)

ASVtaxonomy_CT_RH_2019$Block=as.character(ASVtaxonomy_CT_RH_2019$Block)

RH_CT_data16S_2019 <- inner_join(soil_lab_reduced, ASVtaxonomy_CT_RH_2019, 
                         by = c("Year", "Tillage", "Fertilization", "Block"))
# End Year 2019

# Start Year 2020 
ASVtaxonomy_CT_RH_2020=data.frame(sum=apply(ASVtaxonomy_CT_RH, 2,function(x) sum(x))) %>%
  rownames_to_column(var="Sample") %>%
  full_join(metadata) %>%
  select(Fertilization=Int, everything()) %>%
  filter(Soil_Type=="RH" & Year==2020)

ASVtaxonomy_CT_RH_2020$Block=as.character(ASVtaxonomy_CT_RH_2020$Block)

RH_CT_data16S_2020 <- inner_join(soil_lab_reduced, ASVtaxonomy_CT_RH_2020, 
                         by = c("Year", "Tillage", "Fertilization", "Block"))
# End Year 2020

# Start Year 2021 
ASVtaxonomy_CT_RH_2021=data.frame(sum=apply(ASVtaxonomy_CT_RH, 2,function(x) sum(x))) %>%
  rownames_to_column(var="Sample") %>%
  full_join(metadata) %>%
  select(Fertilization=Int, everything()) %>%
  filter(Soil_Type=="RH" & Year==2021)

ASVtaxonomy_CT_RH_2021$Block=as.character(ASVtaxonomy_CT_RH_2021$Block)

RH_CT_data16S_2021 <- full_join(soil_lab_reduced, ASVtaxonomy_CT_RH_2021, 
                         by = c("Year", "Tillage", "Fertilization", "Block"))%>%
  filter(Soil_Type=="RH" & Year==2021)

# End Year 2021

```

Calculate cumulative relative abundance for MP positive responders for each year in 
root-associated soil
```{r}
all_models_diff_MP_RH=filter(all_models_diff, 
                                        Soil_Type=="RH" &
                                        coeff>0)

ASVtaxonomy_MP_RH=filter(ASVtaxonomy, ASV%in%c(all_models_diff_MP_RH$ASV))%>%
  select(unique(metadata$Sample))

# Start Year 2019 
ASVtaxonomy_MP_RH_2019=data.frame(sum=apply(ASVtaxonomy_MP_RH, 2,function(x) sum(x))) %>%
  rownames_to_column(var="Sample") %>%
  full_join(metadata) %>%
  select(Fertilization=Int, everything()) %>%
  filter(Soil_Type=="RH" & Year==2019)

ASVtaxonomy_MP_RH_2019$Block=as.character(ASVtaxonomy_MP_RH_2019$Block)

RH_MP_data16S_2019 <- inner_join(soil_lab_reduced, ASVtaxonomy_MP_RH_2019, 
                         by = c("Year", "Tillage", "Fertilization", "Block"))%>%
  filter(Soil_Type=="RH" & Year==2019)
# End Year 2019

# Start Year 2020 
ASVtaxonomy_MP_RH_2020=data.frame(sum=apply(ASVtaxonomy_MP_RH, 2,function(x) sum(x))) %>%
  rownames_to_column(var="Sample") %>%
  full_join(metadata) %>%
  select(Fertilization=Int, everything()) %>%
  filter(Soil_Type=="RH" & Year==2020)

ASVtaxonomy_MP_RH_2020$Block=as.character(ASVtaxonomy_MP_RH_2020$Block)

RH_MP_data16S_2020 <- full_join(soil_lab_reduced, ASVtaxonomy_MP_RH_2020, 
                         by = c("Year", "Tillage", "Fertilization", "Block"))%>%
  filter(Soil_Type=="RH" & Year==2020)

# End Year 2020

# Start Year 2021 
ASVtaxonomy_MP_RH_2021=data.frame(sum=apply(ASVtaxonomy_MP_RH, 2,function(x) sum(x))) %>%
  rownames_to_column(var="Sample") %>%
  full_join(metadata) %>%
  select(Fertilization=Int, everything()) %>%
  filter(Soil_Type=="RH" & Year==2021)

ASVtaxonomy_MP_RH_2021$Block=as.character(ASVtaxonomy_MP_RH_2021$Block)

RH_MP_data16S_2021 <- inner_join(soil_lab_reduced, ASVtaxonomy_MP_RH_2021, 
                         by = c("Year", "Tillage", "Fertilization", "Block"))%>%
  filter(Soil_Type=="RH" & Year==2021)

# End Year 2021
```


Calculate cumulative relative abundance for CT positive responders in 
bulk soil
```{r}
# Start Year 2019 
memodel_RAS_CT_2019 <- lm(scale(OM)~scale(sum) , data = RAS_CT_data16S_2019)

boot.out = Boot(memodel_RAS_CT_2019, f=coef, method="residual", R=10000, ncores = 25)
print("Boot  finished")
  
CI.lower = apply(boot.out$t, 2, function(x) as.numeric(quantile(x, probs=.025, na.rm=TRUE)))
CI.upper = apply(boot.out$t, 2, function(x) as.numeric(quantile(x, probs=.975, na.rm=TRUE)))
results_df_RAS_CT_2019 = as.data.frame(summary(boot.out))
p = rbind(
    (1-apply(boot.out$t<0, 2, mean))*2,
    (1-apply(boot.out$t>0, 2, mean))*2)
pvalues=data.frame(pval= apply(p, 2, min))
results_RAS_CT_2019=cbind(results_df_RAS_CT_2019, pvalues, lower=CI.lower, upper=CI.upper)
# End Year 2019

# Start Year 2020
memodel_RAS_CT_2020 <- lm(scale(OM)~scale(sum), data = RAS_CT_data16S_2020)

boot.out = Boot(memodel_RAS_CT_2020, f=coef, method="residual", R=10000, ncores = 25)
print("Boot  finished")
  
CI.lower = apply(boot.out$t, 2, function(x) as.numeric(quantile(x, probs=.025, na.rm=TRUE)))
CI.upper = apply(boot.out$t, 2, function(x) as.numeric(quantile(x, probs=.975, na.rm=TRUE)))
results_df_RAS_CT_2020 = as.data.frame(summary(boot.out))
p = rbind(
    (1-apply(boot.out$t<0, 2, mean))*2,
    (1-apply(boot.out$t>0, 2, mean))*2)
pvalues=data.frame(pval= apply(p, 2, min))
results_RAS_CT_2020=cbind(results_df_RAS_CT_2020, pvalues, lower=CI.lower, upper=CI.upper)
# End Year 2020

# Start Year 2021 
memodel_RAS_CT_2021 <- lm(scale(OM)~scale(sum), data = RAS_CT_data16S_2021)

boot.out = Boot(memodel_RAS_CT_2021, f=coef, method="residual", R=10000, ncores = 25)
print("Boot  finished")
  
CI.lower = apply(boot.out$t, 2, function(x) as.numeric(quantile(x, probs=.025, na.rm=TRUE)))
CI.upper = apply(boot.out$t, 2, function(x) as.numeric(quantile(x, probs=.975, na.rm=TRUE)))
results_df_RAS_CT_2021 = as.data.frame(summary(boot.out))
p = rbind(
    (1-apply(boot.out$t<0, 2, mean))*2,
    (1-apply(boot.out$t>0, 2, mean))*2)
pvalues=data.frame(pval= apply(p, 2, min))
results_RAS_CT_2021=cbind(results_df_RAS_CT_2021, pvalues, lower=CI.lower, upper=CI.upper)
# End Year 2021

#Since p was zero through bootstraps, it was placed as less
# than one divided by the number of bootstraps (10000)
```

Calculate cumulative relative abundance for CT positive responders in 
the rhizosphere
```{r}
# Start Year 2019 
memodel_RH_CT_2019 <- lm(scale(OM)~scale(sum), data = RH_CT_data16S_2019)
#Apply Bootstrap for inferring p-values and 95% CI
boot.out = Boot(memodel_RH_CT_2019, f=coef, method="residual", R=10000, ncores = 25)
print("Boot  finished")
  
CI.lower = apply(boot.out$t, 2, function(x) as.numeric(quantile(x, probs=.025, na.rm=TRUE)))
CI.upper = apply(boot.out$t, 2, function(x) as.numeric(quantile(x, probs=.975, na.rm=TRUE)))
results_df_RH_CT_2019 = as.data.frame(summary(boot.out))
p = rbind(
    (1-apply(boot.out$t<0, 2, mean))*2,
    (1-apply(boot.out$t>0, 2, mean))*2)
pvalues=data.frame(pval= apply(p, 2, min))
results_RH_CT_2019=cbind(results_df_RH_CT_2019, pvalues, lower=CI.lower, upper=CI.upper)
# End Year 2019

# Start Year 2020
memodel_RH_CT_2020 <- lm(scale(OM)~scale(sum), data = RH_CT_data16S_2020)
#Apply Bootstrap for inferring p-values and 95% CI
boot.out = Boot(memodel_RH_CT_2020, f=coef, method="residual", R=10000, ncores = 25)
print("Boot  finished")
  
CI.lower = apply(boot.out$t, 2, function(x) as.numeric(quantile(x, probs=.025, na.rm=TRUE)))
CI.upper = apply(boot.out$t, 2, function(x) as.numeric(quantile(x, probs=.975, na.rm=TRUE)))
results_df_RH_CT_2020 = as.data.frame(summary(boot.out))
p = rbind(
    (1-apply(boot.out$t<0, 2, mean))*2,
    (1-apply(boot.out$t>0, 2, mean))*2)
pvalues=data.frame(pval= apply(p, 2, min))
results_RH_CT_2020=cbind(results_df_RH_CT_2020, pvalues, lower=CI.lower, upper=CI.upper)
# End Year 2020

# Start Year 2021 
memodel_RH_CT_2021 <- lm(scale(OM)~scale(sum), data = RH_CT_data16S_2021)
#Apply Bootstrap for inferring p-values and 95% CI
boot.out = Boot(memodel_RH_CT_2021, f=coef, method="residual", R=10000, ncores = 25)
print("Boot  finished")
  
CI.lower = apply(boot.out$t, 2, function(x) as.numeric(quantile(x, probs=.025, na.rm=TRUE)))
CI.upper = apply(boot.out$t, 2, function(x) as.numeric(quantile(x, probs=.975, na.rm=TRUE)))
results_df_RH_CT_2021 = as.data.frame(summary(boot.out))
p = rbind(
    (1-apply(boot.out$t<0, 2, mean))*2,
    (1-apply(boot.out$t>0, 2, mean))*2)
pvalues=data.frame(pval= apply(p, 2, min))
results_RH_CT_2021=cbind(results_df_RH_CT_2021, pvalues, lower=CI.lower, upper=CI.upper)
# End Year 2021

#Since p was zero through bootstraps, it was placed as less
# than one divided by the number of bootstraps (10000)
```

Calculate cumulative relative abundance for MP positive responders in 
the bulk soil 
```{r}
# Start Year 2019 
memodel_RAS_MP_2019 <- lm(scale(OM)~scale(sum), data = RAS_MP_data16S_2019)
#Apply Bootstrap for inferring p-values and 95% CI
boot.out = Boot(memodel_RAS_MP_2019, f=coef, method="residual", R=10000, ncores = 25)
print("Boot  finished")
  
CI.lower = apply(boot.out$t, 2, function(x) as.numeric(quantile(x, probs=.025, na.rm=TRUE)))
CI.upper = apply(boot.out$t, 2, function(x) as.numeric(quantile(x, probs=.975, na.rm=TRUE)))
results_df_RAS_MP_2019 = as.data.frame(summary(boot.out))
p = rbind(
    (1-apply(boot.out$t<0, 2, mean))*2,
    (1-apply(boot.out$t>0, 2, mean))*2)
pvalues=data.frame(pval= apply(p, 2, min))
results_RAS_MP_2019=cbind(results_df_RAS_MP_2019, pvalues, lower=CI.lower, upper=CI.upper)
# End Year 2019

# Start Year 2020
memodel_RAS_MP_2020 <- lm(scale(OM)~scale(sum), data = RAS_MP_data16S_2020)
#Apply Bootstrap for inferring p-values and 95% CI
boot.out = Boot(memodel_RAS_MP_2020,f=coef, method="residual", R=10000, ncores = 25)
print("Boot  finished")
  
CI.lower = apply(boot.out$t, 2, function(x) as.numeric(quantile(x, probs=.025, na.rm=TRUE)))
CI.upper = apply(boot.out$t, 2, function(x) as.numeric(quantile(x, probs=.975, na.rm=TRUE)))
results_df_RAS_MP_2020 = as.data.frame(summary(boot.out))
p = rbind(
    (1-apply(boot.out$t<0, 2, mean))*2,
    (1-apply(boot.out$t>0, 2, mean))*2)
pvalues=data.frame(pval= apply(p, 2, min))
results_RAS_MP_2020=cbind(results_df_RAS_MP_2020, pvalues, lower=CI.lower, upper=CI.upper)
# End Year 2020

# Start Year 2021 
memodel_RAS_MP_2021 <- lm(scale(OM)~scale(sum), data = RAS_MP_data16S_2021)
#Apply Bootstrap for inferring p-values and 95% CI
boot.out = Boot(memodel_RAS_MP_2021,f=coef, method="residual", R=10000, ncores = 25)
print("Boot  finished")
  
CI.lower = apply(boot.out$t, 2, function(x) as.numeric(quantile(x, probs=.025, na.rm=TRUE)))
CI.upper = apply(boot.out$t, 2, function(x) as.numeric(quantile(x, probs=.975, na.rm=TRUE)))
results_df_RAS_MP_2021 = as.data.frame(summary(boot.out))
p = rbind(
    (1-apply(boot.out$t<0, 2, mean))*2,
    (1-apply(boot.out$t>0, 2, mean))*2)
pvalues=data.frame(pval= apply(p, 2, min))
results_RAS_MP_2021=cbind(results_df_RAS_MP_2021, pvalues, lower=CI.lower, upper=CI.upper)
# End Year 2021

#Since p was zero through bootstraps, it was placed as less
# than one divided by the number of bootstraps (10000)
```

Calculate cumulative relative abundance for MP positive responders in 
the rhizosphere
```{r}
# Start Year 2019 
memodel_RH_MP_2019 <- lm(scale(OM)~scale(sum), data = RH_MP_data16S_2019)
#Apply Bootstrap for inferring p-values and 95% CI
boot.out = Boot(memodel_RH_MP_2019, f=coef, method="residual", R=10000, ncores = 25) 
print("Boot  finished")
  
CI.lower = apply(boot.out$t, 2, function(x) as.numeric(quantile(x, probs=.025, na.rm=TRUE)))
CI.upper = apply(boot.out$t, 2, function(x) as.numeric(quantile(x, probs=.975, na.rm=TRUE)))
results_df_RH_MP_2019 = as.data.frame(summary(boot.out))
p = rbind(
    (1-apply(boot.out$t<0, 2, mean))*2,
    (1-apply(boot.out$t>0, 2, mean))*2)
pvalues=data.frame(pval= apply(p, 2, min))
results_RH_MP_2019=cbind(results_df_RH_MP_2019, pvalues, lower=CI.lower, upper=CI.upper)
 # End Year 2019

# Start Year 2020 
memodel_RH_MP_2020 <- lm(scale(OM)~scale(sum) , data = RH_MP_data16S_2020)
#Apply Bootstrap for inferring p-values and 95% CI
boot.out = Boot(memodel_RH_MP_2020, , f=coef, method="residual", R=10000, ncores = 25)  
print("Boot  finished")
  
CI.lower = apply(boot.out$t, 2, function(x) as.numeric(quantile(x, probs=.025, na.rm=TRUE)))
CI.upper = apply(boot.out$t, 2, function(x) as.numeric(quantile(x, probs=.975, na.rm=TRUE)))
results_df_RH_MP_2020 = as.data.frame(summary(boot.out))
p = rbind(
    (1-apply(boot.out$t<0, 2, mean))*2,
    (1-apply(boot.out$t>0, 2, mean))*2)
pvalues=data.frame(pval= apply(p, 2, min))
results_RH_MP_2020=cbind(results_df_RH_MP_2020, pvalues, lower=CI.lower, upper=CI.upper)
# End Year 2020

# Start Year 2021 
memodel_RH_MP_2021 <-lm(scale(OM)~scale(sum), data = RH_MP_data16S_2021)
#Apply Bootstrap for inferring p-values and 95% CI
boot.out = Boot(memodel_RH_MP_2021, f=coef, method="residual", R=10000, ncores = 25) 
print("Boot  finished")
  
CI.lower = apply(boot.out$t, 2, function(x) as.numeric(quantile(x, probs=.025, na.rm=TRUE)))
CI.upper = apply(boot.out$t, 2, function(x) as.numeric(quantile(x, probs=.975, na.rm=TRUE)))
results_df_RH_MP_2021 = as.data.frame(summary(boot.out))
p = rbind(
    (1-apply(boot.out$t<0, 2, mean))*2,
    (1-apply(boot.out$t>0, 2, mean))*2)
pvalues=data.frame(pval= apply(p, 2, min))
results_RH_MP_2021=cbind(results_df_RH_MP_2021, pvalues, lower=CI.lower, upper=CI.upper)
# End Year 2021

#Since p was zero through bootstraps, it was placed as less
# than one divided by the number of bootstraps (10000)
```

Create all 12 single plots 

```{r}
# Start Year 2019 
plot_results_RAS_CT_2019=ggplot(RAS_CT_data16S_2019, 
  aes(x=100*sum/bac_rer_number,y=OM, fill=as.factor(Fertilization))) +
  geom_point(shape=21, size=2) +
  geom_smooth(method="lm", alpha=0.5) +
  ylab(NULL) +
  xlab("2019: BS CT-responder") +
  theme_bw() +
  scale_fill_brewer(palette="Set3", name="Fertilization: ") +
  
  theme(plot.title=element_text(size=12,colour="black")) + 
  theme(plot.title=element_markdown()) +
 
  theme(strip.background=element_rect(fill="white",colour="black")) +
  
  theme(axis.text.y=element_text(size=10,colour="black")) +
  theme(axis.text.x=element_text(size=10,colour="black")) +
  theme(axis.title.x=element_text(size=12,colour="black")) + 

  theme(legend.text=element_text(size=18,colour="black")) + 
  theme(legend.title=element_text(size=18,colour="black")) + 
  
  ggtitle(paste0("β1 = ",round(results_RAS_CT_2019[2,5],2),
          " [",round(results_RAS_CT_2019[2,7],2),
          ", ",round(results_RAS_CT_2019[2,8],2),
                    "], *p* < 0.0001"))


plot_results_RH_CT_2019=ggplot(RH_CT_data16S_2019, 
  aes(x=100*sum/bac_rer_number,y=OM, fill=as.factor(Fertilization))) +
  geom_point(shape=21, size=2) +
  geom_smooth(method="lm", alpha=0.5) +
  ylab(NULL) +
  xlab("2019: RH CT-responder") +
  theme_bw() +
  scale_fill_brewer(palette="Set3", name="Fertilization: ") +
  
  theme(plot.title=element_text(size=12,colour="black")) +
  theme(plot.title=element_markdown()) +
  
  theme(strip.background=element_rect(fill="white",colour="black")) +
  
  theme(axis.text.y=element_text(size=10,colour="black")) +
  theme(axis.text.x=element_text(size=10,colour="black")) +
  theme(axis.title.x=element_text(size=12,colour="black")) + 
  
  theme(legend.text=element_text(size=18,colour="black")) + 
  theme(legend.title=element_text(size=18,colour="black")) + 
  
  ggtitle(paste0("β1 = ",round(results_RH_CT_2019[2,5],2),
          " [",round(results_RH_CT_2019[2,7],2),
          ", ",round(results_RH_CT_2019[2,8],2),
                    "], *p* < 0.0001")) 

plot_results_RAS_MP_2019=ggplot(RAS_MP_data16S_2019, 
  aes(x=100*sum/bac_rer_number,y=OM, fill=as.factor(Fertilization))) +
  geom_point(shape=21, size=2) +
  geom_smooth(method="lm", alpha=0.5) +
  ylab(NULL) +
  xlab("2019: BS MP-responder") +
  theme_bw() +
  scale_fill_brewer(palette="Set3", name="Fertilization: ") +
  
  theme(plot.title=element_text(size=12,colour="black")) +
  theme(plot.title=element_markdown()) +
  
  theme(strip.background=element_rect(fill="white",colour="black")) +

  theme(axis.text.y=element_text(size=10,colour="black")) +
  theme(axis.text.x=element_text(size=10,colour="black")) +
  theme(axis.title.x=element_text(size=12,colour="black")) + 
  
  theme(legend.text=element_text(size=18,colour="black")) + 
  theme(legend.title=element_text(size=18,colour="black")) + 
  
  ggtitle(paste0("β1 = ",round(results_RAS_MP_2019[2,5],2),
          " [",round(results_RAS_MP_2019[2,7],2),
          ", ",round(results_RAS_MP_2019[2,8],2),
                    "], *p* < 0.0001")) 

plot_results_RH_MP_2019=ggplot(RH_MP_data16S_2019, 
  aes(x=100*sum/bac_rer_number,y=OM, fill=as.factor(Fertilization))) +
  geom_point(shape=21, size=2) +
  geom_smooth(method="lm", alpha=0.5) +
  ylab(NULL) +
  xlab("2019: RH MP-responder") +
  theme_bw() +
  scale_fill_brewer(palette="Set3", name="Fertilization: ") +
  
  theme(plot.title=element_text(size=12,colour="black")) +
  theme(plot.title=element_markdown()) +  
  
  theme(strip.background=element_rect(fill="white", colour="black")) +
  
  theme(axis.text.y=element_text(size=10,colour="black")) +
  theme(axis.text.x=element_text(size=10,colour="black")) +
  theme(axis.title.x=element_text(size=12,colour="black")) + 
  
  theme(legend.text=element_text(size=18,colour="black")) + 
  theme(legend.title=element_text(size=18,colour="black")) + 
  
  ggtitle(paste0("β1 = ",round(results_RH_MP_2019[2,5],2),
          " [",round(results_RH_MP_2019[2,7],2),
          ", ",round(results_RH_MP_2019[2,8],2),
          "], *p* < 0.0001")) 
# End Year 2019

# Start Year 2020 
plot_results_RAS_CT_2020=ggplot(RAS_CT_data16S_2020, 
  aes(x=100*sum/bac_rer_number,y=OM, fill=as.factor(Fertilization))) +
  geom_point(shape=21, size=2) +
  geom_smooth(method="lm", alpha=0.5) +
  ylab(NULL) +
  xlab("2020: BS CT-responder") +
  theme_bw() +
  scale_fill_brewer(palette="Set3", name="Fertilization: ") +
  
  theme(plot.title=element_text(size=12,colour="black")) + 
  theme(plot.title=element_markdown()) +
  
  theme(strip.background=element_rect(fill="white",colour="black")) +

  theme(axis.text.y=element_text(size=10,colour="black")) +
  theme(axis.text.x=element_text(size=10,colour="black")) +
  theme(axis.title.x=element_text(size=12,colour="black")) + 
  
  theme(legend.text=element_text(size=18,colour="black")) + 
  theme(legend.title=element_text(size=18,colour="black")) + 
  
  ggtitle(paste0("β1 = ",round(results_RAS_CT_2020[2,5],2),
          " [",round(results_RAS_CT_2020[2,7],2),
          ", ",round(results_RAS_CT_2020[2,8],2),
                    "], *p* < 0.0001"))


plot_results_RH_CT_2020=ggplot(RH_CT_data16S_2020, 
  aes(x=100*sum/bac_rer_number,y=OM, fill=as.factor(Fertilization))) +
  geom_point(shape=21, size=2) +
  geom_smooth(method="lm", alpha=0.5) +
  ylab(NULL) +
  xlab("2020: RH CT-responder") +
  theme_bw() +
  scale_fill_brewer(palette="Set3", name="Fertilization: ") +
  
  theme(plot.title=element_text(size=12,colour="black")) +
  theme(plot.title=element_markdown()) +
  
  theme(strip.background=element_rect(fill="white",colour="black")) +
  
  theme(axis.text.y=element_text(size=10,colour="black")) +
  theme(axis.text.x=element_text(size=10,colour="black")) +
  theme(axis.title.x=element_text(size=12,colour="black")) + 
  
  theme(legend.text=element_text(size=18,colour="black")) + 
  theme(legend.title=element_text(size=18,colour="black")) + 
  
  ggtitle(paste0("β1 = ",round(results_RH_CT_2020[2,5],2),
          " [",round(results_RH_CT_2020[2,7],2),
          ", ",round(results_RH_CT_2020[2,8],2),
                    "], *p* < 0.0001")) 

plot_results_RAS_MP_2020=ggplot(RAS_MP_data16S_2020, 
  aes(x=100*sum/bac_rer_number,y=OM, fill=as.factor(Fertilization))) +
  geom_point(shape=21, size=2) +
  geom_smooth(method="lm", alpha=0.5) +
  ylab(NULL) +
  xlab("2020: BS MP-responder") +
  theme_bw() +
  scale_fill_brewer(palette="Set3", name="Fertilization: ") +
  
  theme(plot.title=element_text(size=12,colour="black")) +
  theme(plot.title=element_markdown()) +
  
  theme(strip.background=element_rect(fill="white",colour="black")) +
  
  theme(axis.text.y=element_text(size=10,colour="black")) +
  theme(axis.text.x=element_text(size=10,colour="black")) +
  theme(axis.title.x=element_text(size=12,colour="black")) + 
  
  theme(legend.text=element_text(size=18,colour="black")) + 
  theme(legend.title=element_text(size=18,colour="black")) + 
  
  ggtitle(paste0("β1 = ",round(results_RAS_MP_2020[2,5],2),
          " [",round(results_RAS_MP_2020[2,7],2),
          ", ",round(results_RAS_MP_2020[2,8],2),
                    "], *p* < 0.0001")) 


plot_results_RH_MP_2020=ggplot(RH_MP_data16S_2020, 
  aes(x=100*sum/bac_rer_number,y=OM, fill=as.factor(Fertilization))) +
  geom_point(shape=21, size=2) +
  geom_smooth(method="lm", alpha=0.5) +
  ylab(NULL) +
  xlab("2020: RH MP-responder") +
  theme_bw() +
  scale_fill_brewer(palette="Set3", name="Fertilization: ") +
  
  theme(plot.title=element_text(size=12,colour="black")) +
  theme(plot.title=element_markdown()) +
  
  theme(strip.background=element_rect(fill="white", colour="black")) +
  
  theme(axis.text.y=element_text(size=10,colour="black")) +
  theme(axis.text.x=element_text(size=10,colour="black")) +
  theme(axis.title.x=element_text(size=12,colour="black")) + 
  
  theme(legend.text=element_text(size=18,colour="black")) + 
  theme(legend.title=element_text(size=18,colour="black")) + 
  
  ggtitle(paste0("β1 = ",round(results_RH_MP_2020[2,5],2),
          " [",round(results_RH_MP_2020[2,7],2),
          ", ",round(results_RH_MP_2020[2,8],2),
          "], *p* < 0.0001")) 
# End Year 2020

# Start Year 2021 
plot_results_RAS_CT_2021=ggplot(RAS_CT_data16S_2021, 
  aes(x=100*sum/bac_rer_number,y=OM, fill=as.factor(Fertilization))) +
  geom_point(shape=21, size=2) +
  geom_smooth(method="lm", alpha=0.5) +
  ylab(NULL) +
  xlab("2021: BS CT-responder") +
  theme_bw() +
  scale_fill_brewer(palette="Set3", name="Fertilization: ") +
  
  theme(plot.title=element_text(size=12,colour="black")) + 
  theme(plot.title=element_markdown()) +
  
  theme(strip.background=element_rect(fill="white",colour="black")) +
  
  theme(axis.text.y=element_text(size=10,colour="black")) +
  theme(axis.text.x=element_text(size=10,colour="black")) +
  theme(axis.title.x=element_text(size=12,colour="black")) + 
  
  theme(legend.text=element_text(size=18,colour="black")) + 
  theme(legend.title=element_text(size=18,colour="black")) + 
  
  ggtitle(paste0("β1 = ",round(results_RAS_CT_2021[2,5],2),
          " [",round(results_RAS_CT_2021[2,7],2),
          ", ",round(results_RAS_CT_2021[2,8],2),
                    "], *p* < 0.0001"))

plot_results_RH_CT_2021=ggplot(RH_CT_data16S_2021, 
  aes(x=100*sum/bac_rer_number,y=OM, fill=as.factor(Fertilization))) +
  geom_point(shape=21, size=2) +
  geom_smooth(method="lm", alpha=0.5) +
  ylab(NULL) +
  xlab("2021: RH CT-responder") +
  theme_bw() +
  scale_fill_brewer(palette="Set3", name="Fertilization: ") +
  
  theme(plot.title=element_text(size=12,colour="black")) +
  theme(plot.title=element_markdown()) +
  
  theme(strip.background=element_rect(fill="white",colour="black")) +
  
  theme(axis.text.y=element_text(size=10,colour="black")) +
  theme(axis.text.x=element_text(size=10,colour="black")) +
  theme(axis.title.x=element_text(size=12,colour="black")) + 
  
  theme(legend.text=element_text(size=18,colour="black")) + 
  theme(legend.title=element_text(size=18,colour="black")) + 
  
  ggtitle(paste0("β1 = ",round(results_RH_CT_2021[2,5],2),
          " [",round(results_RH_CT_2021[2,7],2),
          ", ",round(results_RH_CT_2021[2,8],2),
                    "], *p* < 0.0001")) 

plot_results_RAS_MP_2021=ggplot(RAS_MP_data16S_2021, 
  aes(x=100*sum/bac_rer_number,y=OM, fill=as.factor(Fertilization))) +
  geom_point(shape=21, size=2) +
  geom_smooth(method="lm", alpha=0.5) +
  ylab(NULL) +
  xlab("2021: BS MP-responder") +
  theme_bw() +
  scale_fill_brewer(palette="Set3", name="Fertilization: ") +
  
  theme(plot.title=element_text(size=12,colour="black")) +
  theme(plot.title=element_markdown()) +
  
  theme(strip.background=element_rect(fill="white",colour="black")) +
  
  theme(axis.text.y=element_text(size=10,colour="black")) +
  theme(axis.text.x=element_text(size=10,colour="black")) +
  theme(axis.title.x=element_text(size=12,colour="black")) + 
  
  theme(legend.text=element_text(size=18,colour="black")) + 
  theme(legend.title=element_text(size=18,colour="black")) + 
  
  ggtitle(paste0("β1 = ",round(results_RAS_MP_2021[2,5],2),
          " [",round(results_RAS_MP_2021[2,7],2),
          ", ",round(results_RAS_MP_2021[2,8],2),
                    "], *p* < 0.0001")) 

plot_results_RH_MP_2021=ggplot(RH_MP_data16S_2021, 
  aes(x=100*sum/bac_rer_number,y=OM, fill=as.factor(Fertilization))) +
  geom_point(shape=21, size=2) +
  geom_smooth(method="lm", alpha=0.5) +
  ylab(NULL) +
  xlab("2021: RH MP-responder") +
  theme_bw() +
  scale_fill_brewer(palette="Set3", name="Fertilization: ") +
  
  theme(plot.title=element_text(size=12,colour="black")) +
  theme(plot.title=element_markdown()) +
  
  theme(strip.background=element_rect(fill="white", colour="black")) +
  
  theme(axis.text.y=element_text(size=10,colour="black")) +
  theme(axis.text.x=element_text(size=10,colour="black")) +
  theme(axis.title.x=element_text(size=12,colour="black")) + 
  
  theme(legend.text=element_text(size=18,colour="black")) + 
  theme(legend.title=element_text(size=18,colour="black")) + 
  
  ggtitle(paste0("β1 = ",round(results_RH_MP_2021[2,5],2),
          " [",round(results_RH_MP_2021[2,7],2),
          ", ",round(results_RH_MP_2021[2,8],2),
          "], *p* < 0.0001")) 
# End Year 2021
```

Combine all plots together
```{r}

# *p* < 0.0001 muss in den Header 
empty_space <- ggplot() + theme_void()

plots <- ggarrange(
    plot_results_RAS_CT_2019, 
    plot_results_RAS_CT_2020, 
    plot_results_RAS_CT_2021, 
    plot_results_RH_CT_2019, 
    plot_results_RH_CT_2020, 
    plot_results_RH_CT_2021, 
    empty_space, empty_space, empty_space, empty_space, empty_space, empty_space,
    plot_results_RAS_MP_2019,
    plot_results_RAS_MP_2020,
    plot_results_RAS_MP_2021,
    plot_results_RH_MP_2019,
    plot_results_RH_MP_2020,
    plot_results_RH_MP_2021,
    empty_space, empty_space, empty_space, empty_space, empty_space, empty_space,
    ncol=6,
    nrow=4,
    common.legend=TRUE,
    legend = "top",
    heights = c(0.8, 0.05, 0.8, 0.05) 
  )

plots_annotated=annotate_figure(plots,
                      bottom=text_grob("Cumulative RA%", color="black", size=14,vjust=-0.5),
                      left=text_grob("SOM[%]",color="black", size = 14, rot=90, vjust=1)
                      )


```
```{r}
png(filename = "Fig3_LinearRegression_revised.png", height = 2500,
    width = 6000, res=300)
print(plots_annotated)
dev.off()
```

```{r}
print("The end!")
```
